---
title: "AMP Manuscript + Exploratory Analysis"
output:
  html_document:
    df_print: paged
  pdf_document:
    latex_engine: xelatex
---

<!-- Summary of analyses:
1) Primary visit-level mixed-effects logistic regression:
   Missed infusion per visit as a function of demographics, country, and arm,
   with random intercepts for participants and adjustment for infusion number.
2) Secondary participant-level logistic regression:
   >=2 missed infusions (missed2plus) ~ age, sex, country, treatment arm, total_infusions.
3) Secondary AE-based visit-level mixed-effects model:
   Risk of missing the next infusion, with AE at prior infusion (AE_prior) as a key predictor.
-->

# 1. Data Setup and Cohort Definition
<!-- This section loads AMP datasets, defines the infusion-visit cohort,
and creates analysis-ready core variables used across all models. -->

```{r setup, message=FALSE}
# Set global chunk behavior for a manuscript-focused output.
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = TRUE)

pkgs <- c(
  "data.table","dplyr","tidyr","purrr","reshape2","xtable",
  "ggplot2","scales","viridisLite","ggpubr",
  "broom","broom.mixed","lme4","MASS","survival","survminer",
  "knitr","tableone","rmarkdown","tinytex"
)

missing_pkgs <- setdiff(pkgs, rownames(installed.packages()))
if (length(missing_pkgs)) {
  stop(paste0(
    "Missing required packages: ",
    paste(missing_pkgs, collapse = ", "),
    ". Install them before knitting this report."
  ))
}

library(data.table); library(tidyr); library(purrr); library(reshape2)
library(ggplot2); library(scales); library(ggpubr)
library(broom); library(broom.mixed); library(lme4)
library(MASS); library(survival); library(survminer)
library(knitr); library(tableone); library(rmarkdown); library(dplyr)
library(xtable)

# Continuous age is the primary representation in the participant-level model.
# Ordered age_bin is used in visit-level models for interpretability.
age_bin_breaks <- c(-Inf, 18, 26, 34, 42, 51, Inf)
age_bin_levels <- c("<18", "18-25", "26-33", "34-41", "42-50", ">50")
age_palette <- c(
  "18-25" = "#F06A61",
  "26-33" = "#79A83B",
  "34-41" = "#43B9C6",
  "42-50" = "#B784E3"
)

fit_mixed_logit <- function(formula, data) {
  fit_primary <- try(
    glmer(
      formula,
      data = data,
      family = binomial(),
      nAGQ = 0,
      control = glmerControl(
        optimizer = "nloptwrap",
        calc.derivs = FALSE,
        optCtrl = list(maxeval = 1e5)
      )
    ),
    silent = TRUE
  )
  if (!inherits(fit_primary, "try-error")) return(fit_primary)

  fit_fallback <- try(
    glmer(
      formula,
      data = data,
      family = binomial(),
      nAGQ = 1,
      control = glmerControl(
        optimizer = "bobyqa",
        calc.derivs = TRUE,
        optCtrl = list(maxfun = 2e5)
      )
    ),
    silent = TRUE
  )
  if (!inherits(fit_fallback, "try-error")) return(fit_fallback)

  stop(
    paste0(
      "Mixed-effects logistic regression failed with both optimizers. ",
      "Primary error: ", as.character(fit_primary), " | ",
      "Fallback error: ", as.character(fit_fallback)
    )
  )
}

tidy_mixed_or <- function(model) {
  as.data.table(broom.mixed::tidy(
    model,
    effects = "fixed",
    conf.int = TRUE,
    conf.method = "Wald",
    exponentiate = TRUE
  ))
}

# Set file paths
# Resolve data files from current working directory or known AMP data locations
resolve_data_file <- function(filename) {
  candidates <- c(
    file.path(getwd(), filename),
    file.path('/Users/joshuamartin/Desktop/untitled folder', filename),
    file.path('/Users/joshuamartin/Desktop/2:17:26 Manuscript Copy -- Rework', filename)
  )
  existing <- candidates[file.exists(candidates)]
  if (length(existing) == 0) {
    stop(paste0(
      'Could not locate ', filename, '. Looked in: ',
      paste(unique(candidates), collapse = '; ')
    ))
  }
  normalizePath(existing[1], winslash = '/', mustWork = TRUE)
}

retention_file <- resolve_data_file('retention.csv')
reacto_file <- resolve_data_file('reacto.csv')
subject_master_file <- resolve_data_file('subject_master.csv')
```

**Explanation:** Checks that required R packages are already installed, loads libraries, defines mixed-effects helper functions, and sets file paths for the analysis.


```{r load-retention, message=FALSE}
# Load retention.csv (visit-level schedule/attendance table)
dt_retention <- fread(retention_file)

# Compact QC summary for manuscript reproducibility
retention_qc <- data.table(
  rows = nrow(dt_retention),
  cols = ncol(dt_retention),
  missing_cells = sum(is.na(dt_retention))
)
kable(retention_qc, caption = "QC Summary: retention.csv")
```

**Explanation:** Opens the retention spreadsheet, prints the data structure, counts missing values, and shows the first few rows so you know what you are working with.


```{r load-reacto, message=FALSE}
# Load reacto.csv (solicited adverse-event table)
dt_reacto <- fread(reacto_file)

# Compact QC summary for manuscript reproducibility
reacto_qc <- data.table(
  rows = nrow(dt_reacto),
  cols = ncol(dt_reacto),
  missing_cells = sum(is.na(dt_reacto))
)
kable(reacto_qc, caption = "QC Summary: reacto.csv")
```

**Explanation:** Opens the adverse event spreadsheet (reacto.csv) and gives the same quick structure, missing-value count, and preview.


```{r merge-data, message=FALSE}
# Load subject_master.csv (participant-level baseline table)
subject_master <- fread(subject_master_file)

# Merge retention and subject_master by protocol and uid
merged_data <- merge(dt_retention, subject_master, by = c("protocol", "uid"), all.x = TRUE)

# Compact QC summary for manuscript reproducibility
merged_qc <- data.table(
  rows = nrow(merged_data),
  cols = ncol(merged_data),
  missing_cells = sum(is.na(merged_data))
)
kable(merged_qc, caption = "QC Summary: merged_data")
```

**Explanation:** Loads the subject roster and merges it with the retention data so every visit record carries the participant demographics.


```{r total-scheduled-visits-by-country1, message=FALSE}
# Total scheduled visits (all visit types) by country
total_scheduled_by_country <- merged_data[
  , .(Total_Scheduled_Visits = .N),
  by = country
][order(-Total_Scheduled_Visits)]

kable(
  total_scheduled_by_country,
  col.names = c("Country", "Total Scheduled Visits"),
  caption = "Total Scheduled Visits by Country"
)
```

**Explanation:** Counts every scheduled visit recorded in `retention.csv` for each country so you can see overall visit volume, regardless of infusion status.


```{r total-scheduled-visits-by-sex, message=FALSE}
# Total scheduled visits (all visit types) by sex
total_scheduled_by_sex <- merged_data[
  !is.na(sex),
  .(Total_Scheduled_Visits = .N),
  by = sex
][order(-Total_Scheduled_Visits)]

kable(
  total_scheduled_by_sex,
  col.names = c("Sex", "Total Scheduled Visits"),
  caption = "Total Scheduled Visits by Sex"
)
```

**Explanation:** Tallies every scheduled visit in `retention.csv` by sex so you can compare overall visit volume between sex categories.

```{r infusions-only, message=FALSE}
# Define infusion visit labels
infusion_labels <- c(
  "Enrollment/Infusion 1",
  "Week 8/Infusion 2",
  "Week 16/Infusion 3",
  "Week 24/Infusion 4",
  "Week 32/Infusion 5",
  "Week 40/Infusion 6",
  "Week 48/Infusion 7",
  "Week 56/Infusion 8",
  "Week 64/Infusion 9",
  "Week 72/Infusion 10"
)

# Filter merged_data for scheduled infusion visits only
infusions_all <- merged_data[visitlabel %in% infusion_labels]

# Methods note (manuscript-ready):
# Primary missed-infusion analyses are restricted to expected scheduled infusion visits.
# Rows recorded after permanent infusion discontinuation are excluded
# (visitday > discday based on participant-level discday from subject_master).
infusions_all[, visitday_num := suppressWarnings(as.numeric(visitday))]
infusions_all[, discday_num := suppressWarnings(as.numeric(discday))]
infusions_all[, post_discontinuation_row := !is.na(discday_num) & !is.na(visitday_num) & visitday_num > discday_num]

# Primary analysis infusion dataset (expected scheduled infusions only)
infusions_only <- infusions_all[post_discontinuation_row == FALSE]

# Create ordered age bins once so all visit-level models share the same coding.
subject_master[, age_bin := cut(
  age,
  breaks = age_bin_breaks,
  labels = age_bin_levels,
  right = FALSE,
  include.lowest = TRUE,
  ordered_result = TRUE
)]
```

**Explanation:** Keeps only the infusion visits from the merged data so the later retention checks focus on treatment visits instead of all study events.

```{r classify-infusion-outcome, message=FALSE}
# Classify each infusion visit outcome
infusions_only[, infusion_outcome := fifelse(attn == "Y" & recv == "Y", "Arrived + Infused",
                                 fifelse(attn == "Y" & recv == "N", "Arrived + Not Infused",
                                 fifelse(attn == "N" & recv == "N", "Did Not Arrive + Not Infused", NA_character_)))]

# missed_infusion_core:
# 1 if an infusion visit was expected but infusion was not administered
# (i.e., any non-"Arrived + Infused" infusion outcome), 0 if infusion was given.
# This is the single core definition used in all downstream "missed infusion" analyses.
# Non-infusion follow-up visits and post-discontinuation infusion rows are not counted here.
infusions_only[, missed_infusion_core := fifelse(infusion_outcome == "Arrived + Infused", 0L, 1L)]

# Canonical analysis keys used in all visit-level mixed models.
infusions_only[, infusion_num := as.integer(gsub(".*Infusion ([0-9]+)", "\\1", visitlabel))]
infusions_only[, participant_id := interaction(protocol, uid, drop = TRUE)]

# Ordered age bins at the infusion-visit level for interpretable mixed models.
infusions_only[, age_bin := cut(
  age,
  breaks = age_bin_breaks,
  labels = age_bin_levels,
  right = FALSE,
  include.lowest = TRUE,
  ordered_result = TRUE
)]

kable(infusions_only[, .N, by = infusion_outcome], caption = "Infusion Outcome Classification")
```

**Explanation:** Labels each infusion visit as infused, arrived but not infused, or missed entirely based on the attendance and infusion columns.

```{r post-discontinuation-impact, message=FALSE}
# Results note (manuscript-ready):
# Excluding post-discontinuation rows had negligible impact on overall missed-infusion estimates.
infusions_all[, missed_all := fifelse(attn == "Y" & recv == "Y", 0L, 1L)]

impact_summary <- data.table(
  dataset = c("Including post-discontinuation rows", "Excluding post-discontinuation rows (primary)"),
  total_rows = c(nrow(infusions_all), nrow(infusions_only)),
  missed_rows = c(sum(infusions_all$missed_all, na.rm = TRUE), sum(infusions_only$missed_infusion_core, na.rm = TRUE))
)
impact_summary[, missed_pct := round(100 * missed_rows / total_rows, 4)]

post_disc_rows <- infusions_all[post_discontinuation_row == TRUE, .N]
post_disc_participants <- infusions_all[post_discontinuation_row == TRUE, uniqueN(interaction(protocol, uid, drop = TRUE))]

kable(
  impact_summary,
  col.names = c("Dataset", "Infusion Rows", "Missed Infusions", "Missed (%)"),
  caption = sprintf(
    "Impact of Excluding Post-Discontinuation Infusion Rows (Rows Excluded = %d; Participants = %d)",
    post_disc_rows, post_disc_participants
  )
)
```

```{r visit-summary-by-sex, message=FALSE}
# Combined scheduled and infusion visit outcomes by sex
scheduled_by_sex <- merged_data[
  !is.na(sex),
  .(Total_Scheduled_Visits = .N),
  by = sex
]

infusion_by_sex <- infusions_only[
  !is.na(sex),
  .(
    Total_Infusion_Visits = .N,
    Infused_Visits = sum(infusion_outcome == "Arrived + Infused", na.rm = TRUE),
    Missed_Infusions = sum(missed_infusion_core == 1L, na.rm = TRUE)
  ),
  by = sex
]

visit_summary_by_sex <- merge(
  scheduled_by_sex,
  infusion_by_sex,
  by = "sex",
  all = TRUE
)[order(-Total_Scheduled_Visits)]

visit_summary_by_sex[, `:=`(
  Infused_Rate = round(Infused_Visits / Total_Infusion_Visits, 3),
  Missed_Rate = round(Missed_Infusions / Total_Infusion_Visits, 3)
)]

kable(
  visit_summary_by_sex,
  col.names = c(
    "Sex",
    "Total Scheduled Visits",
    "Total Infusion Visits",
    "Infused Visits",
    "Missed Infusions",
    "Infused Rate",
    "Missed Rate"
  ),
  caption = "Overall Scheduled and Infusion Visit Outcomes by Sex"
)
```

**Explanation:** Combines the scheduled-visit workload and infusion outcomes for each sex, including the proportion of infusion visits that administered product versus those missed.


```{r visits-and-missed-by-sex, message=FALSE}
# Summarize total infusion visits and missed infusion visits by sex
visits_by_sex <- infusions_only[
  !is.na(sex),
  .(
    Total_Visits = .N,
    Missed_Visits = sum(missed_infusion_core == 1L, na.rm = TRUE)
  ),
  by = sex
][order(-Total_Visits)]

# Missed-visit rate for quick reference
visits_by_sex[, Missed_Rate := round(Missed_Visits / Total_Visits, 3)]

kable(
  visits_by_sex,
  col.names = c("Sex", "Total Infusion Visits", "Missed Infusion Visits", "Missed Rate"),
  caption = "Total and Missed Infusion Visits by Sex"
)
```

**Explanation:** Shows how many infusion visits were scheduled for each sex, how many were missed, and the corresponding missed rate so you can compare adherence across sexes.






```{r age-range-by-protocol, message=FALSE}
# Age range (minimum and maximum) by protocol
age_range_by_protocol <- subject_master[
  !is.na(protocol) & !is.na(age),
  .(
    Min_Age = min(age, na.rm = TRUE),
    Max_Age = max(age, na.rm = TRUE)
  ),
  by = protocol
][order(protocol)]

kable(
  age_range_by_protocol,
  col.names = c("Protocol", "Minimum Age", "Maximum Age"),
  caption = "Age Range of Enrolled Participants by Protocol"
)
```

**Explanation:** Lists each protocol with the youngest and oldest enrolled participant so you can quickly see the age span per protocol.


```{r infused-visits-by-sex, message=FALSE}
# Total infused visits (product received) by sex
infused_by_sex <- infusions_only[
  !is.na(sex),
  .(
    Infused_Visits = sum(infusion_outcome == "Arrived + Infused", na.rm = TRUE),
    Total_Visits = .N
  ),
  by = sex
][order(-Infused_Visits)]

infused_by_sex[, Infused_Rate := round(Infused_Visits / Total_Visits, 3)]

kable(
  infused_by_sex,
  col.names = c("Sex", "Infused Visits", "Total Infusion Visits", "Infused Rate"),
  caption = "Total Infused Visits (Product Received) by Sex"
)
```

**Explanation:** Counts how many infusion visits resulted in product administration for each sex, along with the share of scheduled visits that were infused.


```{r infusion-summary-by-arm, message=FALSE}
# Total infusion visits, infused visits, and missed infusions by treatment arm
infusion_summary_by_arm <- infusions_only[
  !is.na(rx_code),
  .(
    Total_Infusion_Visits = .N,
    Infused_Visits = sum(infusion_outcome == "Arrived + Infused", na.rm = TRUE),
    Missed_Infusions = sum(missed_infusion_core == 1L, na.rm = TRUE)
  ),
  by = rx_code
][order(rx_code)]

infusion_summary_by_arm[, `:=`(
  Infused_Rate = round(Infused_Visits / Total_Infusion_Visits, 3),
  Missed_Rate = round(Missed_Infusions / Total_Infusion_Visits, 3)
)]

kable(
  infusion_summary_by_arm,
  col.names = c(
    "Treatment Arm",
    "Total Infusion Visits",
    "Infused Visits",
    "Missed Infusions",
    "Infused Rate",
    "Missed Rate"
  ),
  caption = "Infusion Visit Outcomes by Treatment Arm"
)
```

**Explanation:** Summarizes each treatment arm’s infusion workload, showing total scheduled infusions, how many administered product, how many were missed, and the corresponding proportions.


```{r visit-summary-by-protocol, message=FALSE}
# Combined scheduled and infusion visit outcomes by protocol
scheduled_by_protocol <- merged_data[
  !is.na(protocol),
  .(Total_Scheduled_Visits = .N),
  by = protocol
]

infusion_by_protocol <- infusions_only[
  !is.na(protocol),
  .(
    Total_Infusion_Visits = .N,
    Infused_Visits = sum(infusion_outcome == "Arrived + Infused", na.rm = TRUE),
    Missed_Infusions = sum(missed_infusion_core == 1L, na.rm = TRUE)
  ),
  by = protocol
]

visit_summary_by_protocol <- merge(
  scheduled_by_protocol,
  infusion_by_protocol,
  by = "protocol",
  all = TRUE
)[order(-Total_Scheduled_Visits)]

visit_summary_by_protocol[, `:=`(
  Infused_Rate = round(Infused_Visits / Total_Infusion_Visits, 3),
  Missed_Rate = round(Missed_Infusions / Total_Infusion_Visits, 3)
)]

kable(
  visit_summary_by_protocol,
  col.names = c(
    "Protocol",
    "Total Scheduled Visits",
    "Total Infusion Visits",
    "Infused Visits",
    "Missed Infusions",
    "Infused Rate",
    "Missed Rate"
  ),
  caption = "Overall Scheduled and Infusion Visit Outcomes by Protocol"
)
```

**Explanation:** Provides the per-protocol workload across all scheduled visits, the infusion visit subset, and the infused versus missed outcomes with their proportions.

# 2. Baseline Characteristics (Table 1)
<!-- This section summarizes baseline participant characteristics used as model covariates
and outputs manuscript Table 1 for the adherence analysis cohort. -->

```{r demographics-summary, message=FALSE}
# Baseline characteristics (Table 1):
# Demographic and clinical characteristics (age, age_bin, sex, race/ethnicity,
# country, treatment arm, protocol) for participants included in adherence analyses.
table1_data <- copy(subject_master)
table1_data <- table1_data[!is.na(protocol) & !is.na(uid)]
table1_data[, age_bin := cut(
  age,
  breaks = age_bin_breaks,
  labels = age_bin_levels,
  right = FALSE,
  include.lowest = TRUE,
  ordered_result = TRUE
)]

table1_vars <- c("age", "age_bin", "sex", "race", "ethnicity", "country", "rx_code", "protocol")
baseline_table1 <- CreateTableOne(vars = table1_vars, data = table1_data)
kable(
  print(baseline_table1, showAllLevels = TRUE),
  caption = "Table 1. Baseline Demographics and Study Characteristics (All Participants)"
)
```

**Explanation:** Builds an overall demographics table (age, sex, country, treatment arm) for the study population.


```{r demographics-by-arm, message=FALSE, eval=FALSE}
# Demographics summary stratified by treatment arm (rx_code), and optionally by country and sex
# By treatment arm only
summary_by_arm <- CreateTableOne(vars = c("age", "sex", "country"), strata = "rx_code", data = subject_demo)
print(summary_by_arm, showAllLevels = TRUE)

# Optionally, by treatment arm and country
summary_by_arm_country <- CreateTableOne(vars = c("age", "sex"), strata = c("rx_code", "country"), data = subject_demo)
print(summary_by_arm_country, showAllLevels = TRUE)

# Optionally, by treatment arm and sex
summary_by_arm_sex <- CreateTableOne(vars = c("age", "country"), strata = c("rx_code", "sex"), data = subject_demo)
print(summary_by_arm_sex, showAllLevels = TRUE)
```

**Explanation:** Repeats the demographics table but splits it by treatment arm, and optionally by arm-with-country or arm-with-sex, so you can see balance between groups.


```{r sex-by-arm, message=FALSE, eval=FALSE}
# Contingency table of Sex by Treatment Arm
sex_arm_table <- table(subject_master$sex, subject_master$rx_code)
print(sex_arm_table)

# Chi-squared test
sex_arm_chisq <- chisq.test(sex_arm_table)
print(sex_arm_chisq)
```

**Explanation:** Creates a sex-by-treatment contingency table and runs a chi-squared test to check whether sex distribution differs across arms.


```{r country-by-arm, message=FALSE, eval=FALSE}
# Contingency table of Country by Treatment Arm
country_arm_table <- table(subject_master$country, subject_master$rx_code)
print(country_arm_table)

# Chi-squared test
country_arm_chisq <- chisq.test(country_arm_table)
print(country_arm_chisq)
```

**Explanation:** Creates a country-by-treatment table and chi-squared test to see if any country is over- or under-represented within an arm.


```{r race-by-arm, message=FALSE, warning=FALSE}
# Contingency table of Race by Treatment Arm (unique participants)
race_arm_table <- table(subject_master$race, subject_master$rx_code)
print(race_arm_table)

# Prefer chi-squared; fall back to Fisher with simulation for sparse cells
race_chi <- suppressWarnings(chisq.test(race_arm_table))
if (any(race_chi$expected < 5)) {
  race_arm_test <- fisher.test(race_arm_table, simulate.p.value = TRUE, B = 10000)
} else {
  race_arm_test <- race_chi
}
print(race_arm_test)

kable(race_arm_table, caption = "Race Distribution by Treatment Arm")
```

**Explanation:** Creates a race-by-treatment table plus chi-squared test, then prints a nicely formatted version for reporting.


```{r ethnicity-by-arm, message=FALSE, warning=FALSE}
# Contingency table of Ethnicity by Treatment Arm (unique participants)
ethnicity_arm_table <- table(subject_master$ethnicity, subject_master$rx_code)
print(ethnicity_arm_table)

# Prefer chi-squared; fall back to Fisher with simulation for sparse cells
eth_chi <- suppressWarnings(chisq.test(ethnicity_arm_table))
if (any(eth_chi$expected < 5)) {
  ethnicity_arm_test <- fisher.test(ethnicity_arm_table, simulate.p.value = TRUE, B = 10000)
} else {
  ethnicity_arm_test <- eth_chi
}
print(ethnicity_arm_test)

kable(ethnicity_arm_table, caption = "Ethnicity Distribution by Treatment Arm")
```

**Explanation:** Does the same for ethnicity, highlighting whether any arm has noticeably different ethnicity makeup.


```{r age-barplot-by-arm, message=FALSE}
# ggplot2 loaded in setup

# Ordered age-bin coding used for all visit-level age-stratified analyses.
subject_master$age_bin <- cut(
  subject_master$age,
  breaks = age_bin_breaks,
  labels = age_bin_levels,
  right = FALSE,
  include.lowest = TRUE,
  ordered_result = TRUE
)

# Bar plot
p <- ggplot(subject_master, aes(x = age_bin, fill = rx_code)) +
  geom_bar(position = position_dodge(width = 0.9)) +
  geom_text(stat = "count", aes(label = after_stat(count)), position = position_dodge(width = 0.9), vjust = -0.2, size = 3) +
  labs(title = "Age Distribution by Treatment Arm",
       x = "Age Range (years)",
       y = "Count",
       fill = "Treatment Arm",
       caption = "Age bins: <18, 18-25, 26-33, 34-41, 42-50, >50") +
  theme_minimal()

print(p)
```

**Explanation:** Bins ages into ranges and draws a bar chart that compares how many people in each age band fall into each treatment arm.


```{r age-table-by-arm, message=FALSE}
# knitr loaded in setup

# Create a table of age distribution by treatment arm
age_table <- table(subject_master$age_bin, subject_master$rx_code)
age_table_df <- as.data.frame.matrix(age_table)
age_table_df$Age_Bin <- rownames(age_table_df)
age_table_df <- age_table_df[, c("Age_Bin", setdiff(names(age_table_df), "Age_Bin"))]

kable(age_table_df, caption = "Age Distribution by Treatment Arm (Age bins: <18, 18-25, 26-33, 34-41, 42-50, >50)")
```

**Explanation:** Turns the age-bin counts into a table so you can cite the exact numbers in each arm and age band.


```{r country-table-by-arm, message=FALSE}
# knitr loaded in setup

# Create a table of country distribution by treatment arm
country_table <- table(subject_master$country, subject_master$rx_code)
country_table_df <- as.data.frame.matrix(country_table)
country_table_df$Country <- rownames(country_table_df)
country_table_df <- country_table_df[, c("Country", setdiff(names(country_table_df), "Country"))]

kable(country_table_df, caption = "Country Distribution by Treatment Arm")
```

**Explanation:** Builds a country-by-arm table in a reader-friendly format.


```{r sex-table-by-arm, message=FALSE}
# knitr loaded in setup

# Create a table of sex distribution by treatment arm
sex_table <- table(subject_master$sex, subject_master$rx_code)
sex_table_df <- as.data.frame.matrix(sex_table)
sex_table_df$Sex <- rownames(sex_table_df)
sex_table_df <- sex_table_df[, c("Sex", setdiff(names(sex_table_df), "Sex"))]

kable(sex_table_df, caption = "Sex Distribution by Treatment Arm")
```

**Explanation:** Builds a sex-by-arm table in a reader-friendly format.


```{r add-age-bin-to-infusions, message=FALSE}
# Ensure age_bin exists in infusions_only
tmp_age <- infusions_only$age
infusions_only$age_bin <- cut(
  tmp_age,
  breaks = age_bin_breaks,
  labels = age_bin_levels,
  right = FALSE,
  include.lowest = TRUE,
  ordered_result = TRUE
)
```

**Explanation:** Copies each participant’s age band onto every infusion visit so future summaries can be grouped by age.


```{r missed-infusion-rate-by-age, message=FALSE}
# Calculate missed infusion rate by age group
missed_by_age <- infusions_only[, .(
  total_infusions = .N,
  missed_infusions = sum(missed_infusion_core == 1L, na.rm = TRUE),
  missed_rate = mean(missed_infusion_core == 1L, na.rm = TRUE)
), by = age_bin]

# knitr loaded in setup
kable(missed_by_age, digits = 3, caption = "Missed Infusion Rate by Age Group (age_bin)")
```

**Explanation:** Counts, for each age band, how many infusions were scheduled, how many were missed, and what percent of visits were missed.



```{r missed-infusion-counts, message=FALSE}
# Calculate number of missed infusions per participant
missed_counts <- infusions_only[, .(missed = sum(missed_infusion_core == 1L, na.rm = TRUE)), by = .(protocol, uid)]

# Categorize participants by number of missed infusions
missed_counts[, missed_cat := fifelse(missed == 0, "0 missed",
                               fifelse(missed == 1, "1 missed", 
                               "2 or more missed"))]

# Count number of participants in each category
missed_summary <- missed_counts[, .N, by = missed_cat][order(missed_cat)]

# knitr loaded in setup
kable(missed_summary, col.names = c("Missed Infusions", "Number of Participants"), caption = "Participants by Number of Missed Infusions")
```

**Explanation:** Totals how many infusions each participant missed and bins people into 0, 1, or 2+ misses.


```{r missed-infusion-barplot, message=FALSE}
# ggplot2 loaded in setup

# Bar plot of participants by missed infusion category
p_missed <- ggplot(missed_summary, aes(x = missed_cat, y = N, fill = missed_cat)) +
  geom_bar(stat = "identity", width = 0.7) +
  geom_text(aes(label = N), vjust = -0.3, size = 4) +
  labs(title = "Number of Participants by Missed Infusion Category",
       x = "Missed Infusions",
       y = "Number of Participants") +
  theme_minimal() +
  theme(legend.position = "none")

print(p_missed)
```

**Explanation:** Plots the counts from the previous step so you can visually see how many people fall into each missed category.



```{r missed-infusion-trends, message=FALSE}
# Extract infusion number from visitlabel
infusions_only[, infusion_num := as.integer(gsub(".*Infusion ([0-9]+)", "\\1", visitlabel))]

# Summarize missed infusions by infusion number
missed_by_infusion <- infusions_only[, .(
  total = .N,
  missed = sum(missed_infusion_core == 1L, na.rm = TRUE),
  missed_pct = mean(missed_infusion_core == 1L, na.rm = TRUE)
), by = infusion_num][order(infusion_num)]

# knitr loaded in setup
kable(missed_by_infusion, digits = 3, caption = "Missed Infusions by Infusion Number (across all participants)")
```

**Explanation:** Summarizes total visits, missed visits, and the missed percentage at each infusion number (1 through 10).



```{r missed-infusion-counts-simple, message=FALSE}
# Calculate number of missed infusions per participant
missed_counts <- infusions_only[, .(missed = sum(missed_infusion_core == 1L, na.rm = TRUE)), by = .(protocol, uid)]

# Categorize participants by number of missed infusions
missed_counts[, missed_cat := fifelse(missed == 0, "0 missed",
                               fifelse(missed == 1, "1 missed", 
                               "2 or more missed"))]

# Count number of participants in each category
missed_summary <- missed_counts[, .N, by = missed_cat][order(missed_cat)]

# knitr loaded in setup
kable(missed_summary, col.names = c("Missed Infusions", "Number of Participants"), caption = "Participants by Number of Missed Infusions")
```

**Explanation:** Recomputes the participant-level missed categories (0, 1, 2+) for easy reference in tables.



```{r missed-infusion-rate-barplot, message=FALSE}
# ggplot2 loaded in setup

# Bar plot of missed infusion rate by infusion number
p_missed_rate <- ggplot(missed_by_infusion, aes(x = factor(infusion_num), y = missed_pct)) +
  geom_bar(stat = "identity", fill = "#0073C2FF", width = 0.7) +
  geom_text(aes(label = missed), vjust = -0.3, size = 4) +
  labs(title = "Missed Infusion Rate by Infusion Number",
       x = "Infusion Number",
       y = "Missed Infusion Rate",
       caption = "Number above each bar = missed infusions") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_minimal()

print(p_missed_rate)
```

**Explanation:** Draws a bar chart of the missed percentage at each infusion number and labels the number of misses on top of each bar.



```{r figure-1-stacked-missed-vs-infused, message=FALSE, fig.cap="Figure 1. Infusion visit outcomes by infusion number (visit-level). Stacked bars show attended-and-infused versus missed scheduled infusion visits at each infusion number."}
# Prepare data for stacked bar chart
missed_vs_infused <- infusions_only[, .(
  missed = sum(missed_infusion_core == 1L, na.rm = TRUE),
  arrived_infused = sum(infusion_outcome == "Arrived + Infused", na.rm = TRUE)
), by = infusion_num][order(infusion_num)]

# Convert to long format for stacking
# tidyr loaded in setup
missed_vs_infused_long <- missed_vs_infused %>%
  pivot_longer(cols = c(missed, arrived_infused), names_to = "Outcome", values_to = "Count")

# Label for legend
missed_vs_infused_long$Outcome <- factor(missed_vs_infused_long$Outcome, levels = c("arrived_infused", "missed"), labels = c("Arrived + Infused", "Missed"))

# Figure 1 (primary visit-level descriptive figure): infusion outcomes by infusion number.
p_stacked <- ggplot(missed_vs_infused_long, aes(x = factor(infusion_num), y = Count, fill = Outcome)) +
  geom_bar(stat = "identity") +
  labs(title = "Infusion Visit Outcomes by Infusion Number (Visit-Level)",
       x = "Infusion Number",
       y = "Number of Scheduled Infusion Visits",
       fill = "Outcome") +
  theme_minimal()
print(p_stacked)
```

**Explanation:** Creates a stacked bar chart showing, for each infusion number, how many visits were infused versus missed.



```{r stacked-missed-vs-infused-table, message=FALSE}
# knitr loaded in setup
missed_vs_infused_table <- missed_vs_infused[, .(
  Infusion_Number = infusion_num,
  Arrived_Infused = arrived_infused,
  Missed = missed
)]
kable(missed_vs_infused_table, col.names = c("Infusion Number", "Arrived + Infused", "Missed"), caption = "Infusion Visit Outcomes by Infusion Number")
```

**Explanation:** Shows the exact numbers that feed the stacked bar chart (arrived/infused vs missed at each infusion).



```{r missed-infusion-by-age-over-time, message=FALSE}
# Calculate missed infusions by infusion number and age group
missed_by_infusion_age <- infusions_only[, .(
  total = .N,
  missed = sum(missed_infusion_core == 1L, na.rm = TRUE),
  missed_pct = mean(missed_infusion_core == 1L, na.rm = TRUE)
), by = .(infusion_num, age_bin)][order(infusion_num, age_bin)]

# knitr loaded in setup
kable(missed_by_infusion_age, digits = 3, caption = "Missed Infusions by Infusion Number and Age Group")
```

**Explanation:** Creates a table of missed counts and percentages for every combination of infusion number and age band.



```{r obs-count-by-age-infusion, message=FALSE}
# Table of number of observations per age group and infusion number
obs_count <- infusions_only[, .N, by = .(age_bin, infusion_num)][order(age_bin, infusion_num)]
# knitr loaded in setup
kable(obs_count, col.names = c("Age Group", "Infusion Number", "Number of Observations"), caption = "Number of Observations per Age Group and Infusion Number")
```

**Explanation:** Lists how many observations you actually have for each age band at each infusion so you can judge whether sample sizes are adequate.



```{r missed-infusion-trend-lineplot, message=FALSE}
# ggplot2 loaded in setup

# Use binom.test for CI when counts are small
missed_by_infusion_age[, ci := mapply(function(miss, tot) {
  binom.test(miss, tot)$conf.int[2]  # upper 95% CI
}, missed, total)]
missed_by_infusion_age[, ci_lower := mapply(function(miss, tot) {
  binom.test(miss, tot)$conf.int[1]  # lower 95% CI
}, missed, total)]

# Exclude <18 and >50 age groups from the plot
data_plot <- missed_by_infusion_age[!age_bin %in% c("<18", ">50")]

# Line plot with confidence intervals
p_trend <- ggplot(data_plot, aes(x = infusion_num, y = missed_pct, color = age_bin, group = age_bin)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci, fill = age_bin), alpha = 0.2, color = NA) +
  scale_color_manual(values = age_palette, breaks = names(age_palette)) +
  scale_fill_manual(values = age_palette, breaks = names(age_palette)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(breaks = 1:10) +
  labs(title = "Missed Infusion Trends Over Time by Age Group (18-50)",
       x = "Infusion Number",
       y = "Missed Infusion Rate",
       color = "Age Group",
       fill = "Age Group") +
  theme_minimal()

print(p_trend)
```

**Explanation:** Plots the missed percentage over infusion number for each age band (18–50) and shades the confidence intervals, so you can see trends over time.



```{r missed-infusion-trend-barchart, message=FALSE}
# ggplot2 loaded in setup

# Bar chart of missed infusion rate by infusion number and age group (with CIs)
p_bar <- ggplot(data_plot, aes(x = factor(infusion_num), y = missed_pct, fill = age_bin)) +
  geom_bar(stat = "identity", position = position_dodge(width = 1.0), width = 1.0) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci), position = position_dodge(width = 0.9), width = 0.3) +
  scale_fill_manual(values = age_palette, breaks = names(age_palette)) +
  labs(title = "Missed Infusion Rate by Infusion Number and Age Group (18-50)",
       x = "Infusion Number",
       y = "Missed Infusion Rate",
       fill = "Age Group") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_minimal()

print(p_bar)
```

**Explanation:** Shows the same information as grouped bars with error bars, which can be easier to read for some audiences.



```{r total-missed-infusion-by-age-bar, message=FALSE}
# ggplot2 loaded in setup

# Summarize missed infusions by age group (excluding <18 and >50)
missed_by_agegroup <- infusions_only[!age_bin %in% c("<18", ">50"), .(
  total = .N,
  missed = sum(missed_infusion_core == 1L, na.rm = TRUE),
  missed_rate = mean(missed_infusion_core == 1L, na.rm = TRUE)
), by = age_bin]

# Binomial confidence intervals for missed_rate
missed_by_agegroup[, ci := mapply(function(miss, tot) binom.test(miss, tot)$conf.int[2], missed, total)]
missed_by_agegroup[, ci_lower := mapply(function(miss, tot) binom.test(miss, tot)$conf.int[1], missed, total)]

# Bar chart
p_age_bar <- ggplot(missed_by_agegroup, aes(x = age_bin, y = missed_rate, fill = age_bin)) +
  geom_bar(stat = "identity", width = 0.7) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci), width = 0.2) +
  geom_text(aes(label = missed, y = missed_rate / 2), vjust = 0.5, size = 4) +
  scale_fill_manual(values = age_palette, breaks = names(age_palette)) +
  labs(title = "Total Missed Infusion Rate by Age Group (18-50)",
       x = "Age Group",
       y = "Missed Infusion Rate",
       fill = "Age Group",
       caption = "Number above each bar = total n (missed infusions)") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_minimal() +
  theme(legend.position = "none")

print(p_age_bar)
```

**Explanation:** Aggregates all infusions within each age band (18–50) to show the overall missed rate and its confidence interval, labeling how many misses occurred.



```{r identify-early-discontinuation, message=FALSE}
# 1. Find the last attended infusion for each participant
last_attended <- infusions_only[attn == "Y", .(last_attended_infusion = max(infusion_num, na.rm = TRUE)), by = .(protocol, uid)]

# 2. Merge this info back to all infusion records
infusions_with_last <- merge(infusions_only, last_attended, by = c("protocol", "uid"), all.x = TRUE)

# 3. Flag records after last attended infusion
infusions_with_last[, after_last_attend := infusion_num > last_attended_infusion]

# 4. For each participant, check if all after_last_attend records are "Did Not Arrive + Not Infused"
discontinued <- infusions_with_last[after_last_attend == TRUE, 
  .(all_missed = all(infusion_outcome == "Did Not Arrive + Not Infused")), 
  by = .(protocol, uid, last_attended_infusion)]

# 5. Participants who discontinued (all subsequent visits are missed)
discontinued_participants <- discontinued[all_missed == TRUE]

# 6. Optional: Summarize by infusion number at which discontinuation occurred
# knitr loaded in setup
summary_discontinued <- discontinued_participants[, .N, by = last_attended_infusion][order(last_attended_infusion)]
kable(summary_discontinued, col.names = c("Last Attended Infusion", "Number of Discontinuations"),
      caption = "Number of Participants Discontinuing at Each Infusion Number")
```

**Explanation:** Finds the last infusion each participant attended, flags anyone who missed every subsequent visit, and reports how many people dropped off after each infusion.



```{r early-termination-reasons, message=FALSE}
# Overall early termination reasons (exclude NA/blank entries)
early_termination_reasons <- subject_master[
  !is.na(earlytmreas) & nzchar(trimws(earlytmreas)),
  .(Count = .N),
  by = earlytmreas
][order(-Count)]

early_termination_reasons[, Percent := round(100 * Count / sum(Count), 1)]

kable(
  early_termination_reasons,
  col.names = c("Early Termination Reason", "Count", "Percent"),
  caption = "Overall Early Termination Reasons (Non-missing)"
)
```

**Explanation:** Summarizes the recorded early termination reasons while dropping NA or blank entries, and adds percentages for context.


```{r early-termination-reasons-latex, message=FALSE, results='asis'}
# Generate LaTeX table using xtable
early_termination_xtable <- copy(early_termination_reasons)
setnames(
  early_termination_xtable,
  c("earlytmreas", "Count", "Percent"),
  c("Early Termination Reason", "Count", "Percent")
)

print(
  xtable(
    early_termination_xtable,
    caption = "Overall Early Termination Reasons (Non-missing)",
    label = "tab:early-termination-reasons"
  ),
  include.rownames = FALSE,
  caption.placement = "top",
  align = c("l", "l", "r", "r")
)
```

**Explanation:** Converts the cleaned early-termination summary into a LaTeX-formatted table via `xtable`, ready for inclusion in PDF outputs.

## Baseline Supplementary Displays (Exploratory)
<!-- EXPLORATORY: legacy baseline display chunks retained for reference. -->

```{r overall-demographics-summary, message=FALSE, eval=FALSE}
# knitr loaded in setup

# Age summary
age_summary <- data.frame(
  Median = median(subject_master$age, na.rm = TRUE),
  Q1 = quantile(subject_master$age, 0.25, na.rm = TRUE),
  Q3 = quantile(subject_master$age, 0.75, na.rm = TRUE),
  Mean = mean(subject_master$age, na.rm = TRUE),
  SD = sd(subject_master$age, na.rm = TRUE)
)
kable(age_summary, caption = "Summary Statistics for Age (Median, Q1, Q3, Mean, SD)")

# Sex frequency table
sex_table <- as.data.frame(table(subject_master$sex))
kable(sex_table, col.names = c("Sex", "Count"), caption = "Sex Distribution")

# Country frequency table
country_table <- as.data.frame(table(subject_master$country))
kable(country_table, col.names = c("Country", "Count"), caption = "Country Distribution")
```

**Explanation:** Calculates median, quartiles, mean, and standard deviation for age so you have the basic summary stats in a table.



# Demographics by Treatment Arm

```{r demographics-by-arm-detailed, message=FALSE, eval=FALSE}
# knitr loaded in setup

# Age summary by treatment arm
demog_by_arm <- subject_master[, .(
  Median = as.numeric(median(age, na.rm = TRUE)),
  Q1 = as.numeric(quantile(age, 0.25, na.rm = TRUE)),
  Q3 = as.numeric(quantile(age, 0.75, na.rm = TRUE)),
  Mean = as.numeric(mean(age, na.rm = TRUE)),
  SD = as.numeric(sd(age, na.rm = TRUE))
), by = rx_code]
kable(demog_by_arm, caption = "Summary Statistics for Age by Treatment Arm (Median, Q1, Q3, Mean, SD)")

# Sex frequency by treatment arm
sex_by_arm <- as.data.frame(table(subject_master$rx_code, subject_master$sex))
colnames(sex_by_arm) <- c("Treatment Arm", "Sex", "Count")
kable(sex_by_arm, caption = "Sex Distribution by Treatment Arm")

# Country frequency by treatment arm
country_by_arm <- as.data.frame(table(subject_master$rx_code, subject_master$country))
colnames(country_by_arm) <- c("Treatment Arm", "Country", "Count")
kable(country_by_arm, caption = "Country Distribution by Treatment Arm")
```

**Explanation:** Repeats the age summary (median, quartiles, mean, SD) separately for each treatment arm to compare distributions.


```{r sex-arm-chisq, message=FALSE, eval=FALSE}
# Chi-squared test for sex vs treatment arm
sex_arm_table <- table(subject_master$sex, subject_master$rx_code)
chisq_sex_arm <- chisq.test(sex_arm_table)
sex_arm_table # Show contingency table
chisq_sex_arm # Show test result
```

**Explanation:** Shows the sex-by-arm table again and prints the chi-squared test output so you can reference both numbers and p-value in one spot.


```{r country-arm-chisq, message=FALSE, eval=FALSE}
# Chi-squared test for country vs treatment arm
country_arm_table <- table(subject_master$country, subject_master$rx_code)
chisq_country_arm <- chisq.test(country_arm_table)
country_arm_table # Show contingency table
chisq_country_arm # Show test result
```

**Explanation:** Shows the country-by-arm table and chi-squared test output together.


```{r age-bin-by-arm-table, message=FALSE, eval=FALSE}
# knitr loaded in setup
# Table of age distribution by treatment arm (age_bin)
age_bin_arm_table <- table(subject_master$rx_code, subject_master$age_bin)
age_bin_arm_df <- as.data.frame.matrix(age_bin_arm_table)
age_bin_arm_df$`Treatment Arm` <- rownames(age_bin_arm_df)
age_bin_arm_df <- age_bin_arm_df[, c("Treatment Arm", setdiff(names(age_bin_arm_df), "Treatment Arm"))]
kable(age_bin_arm_df, caption = "Age Distribution by Treatment Arm (Age Bins)")
```

**Explanation:** Creates a table whose rows are treatment arms and columns are age bins, helpful for some table layouts.


```{r sex-arm-table, message=FALSE, eval=FALSE}
# knitr loaded in setup
# dplyr loaded in setup
# Table for sex by treatment arm with percentages
sex_arm_df <- as.data.frame(sex_arm_table)
colnames(sex_arm_df) <- c("Sex", "Treatment Arm", "Count")
sex_arm_df <- sex_arm_df %>% group_by(`Treatment Arm`) %>% mutate(Percent = round(Count / sum(Count) * 100, 1))
sex_arm_df <- as.data.frame(sex_arm_df)
kable(sex_arm_df, col.names = c("Sex", "Treatment Arm", "Count", "Percent"), caption = "Sex Distribution by Treatment Arm (with Percentages)")
```

**Explanation:** Adds percentages to the sex-by-arm table so you can quickly see proportions, not just counts.


```{r country-arm-table, message=FALSE, eval=FALSE}
# knitr loaded in setup
# dplyr loaded in setup
# Table for country by treatment arm with percentages
country_arm_df <- as.data.frame(country_arm_table)
colnames(country_arm_df) <- c("Country", "Treatment Arm", "Count")
country_arm_df <- country_arm_df %>% group_by(`Treatment Arm`) %>% mutate(Percent = round(Count / sum(Count) * 100, 1))
country_arm_df <- as.data.frame(country_arm_df)
kable(country_arm_df, col.names = c("Country", "Treatment Arm", "Count", "Percent"), caption = "Country Distribution by Treatment Arm (with Percentages)")
```

**Explanation:** Adds percentages to the country-by-arm table for the same reason.



# 3. Participant-Level Adherence Outcomes (>=2 Missed Infusions)
<!-- This section defines the binary participant-level endpoint (missed2plus),
summarizes missed counts descriptively, and fits a secondary participant-level logistic model. -->

```{r participant-level-descriptive, message=FALSE}
# Descriptive participant-level adherence categories from the core missed definition.
missed_counts_primary <- infusions_only[
  ,
  .(
    missed = sum(missed_infusion_core, na.rm = TRUE),
    total_infusions = .N
  ),
  by = .(protocol, uid)
]
missed_counts_primary[, missed2plus := as.integer(missed >= 2)]
missed_counts_primary[, missed_cat := fifelse(missed == 0, "0 missed", fifelse(missed == 1, "1 missed", "2+ missed"))]

participant_missed_summary <- missed_counts_primary[, .N, by = missed_cat][order(missed_cat)]
kable(participant_missed_summary, col.names = c("Missed Infusions", "Number of Participants"),
      caption = "Participant-Level Missed Infusion Categories")

missed_counts_cov_desc <- merge(
  missed_counts_primary,
  subject_master[, .(protocol, uid, rx_code)],
  by = c("protocol", "uid"),
  all.x = TRUE
)

# Secondary descriptive comparison: distribution of participant missed counts by arm/protocol.
missed_dist_by_arm <- missed_counts_cov_desc[, .(
  Median_Missed = as.numeric(median(missed, na.rm = TRUE)),
  IQR_Missed = as.numeric(IQR(missed, na.rm = TRUE))
), by = rx_code]
missed_dist_by_protocol <- missed_counts_cov_desc[, .(
  Median_Missed = as.numeric(median(missed, na.rm = TRUE)),
  IQR_Missed = as.numeric(IQR(missed, na.rm = TRUE))
), by = protocol]
kruskal_missed_by_arm <- kruskal.test(missed ~ rx_code, data = missed_counts_cov_desc)
kruskal_missed_by_protocol <- kruskal.test(missed ~ protocol, data = missed_counts_cov_desc)

kable(missed_dist_by_arm, caption = "Median [IQR] Missed Infusions by Treatment Arm")
kable(missed_dist_by_protocol, caption = "Median [IQR] Missed Infusions by Protocol")
kable(
  data.table(
    Comparison = c("Missed count by treatment arm", "Missed count by protocol"),
    P_value = c(kruskal_missed_by_arm$p.value, kruskal_missed_by_protocol$p.value)
  ),
  caption = "Kruskal-Wallis Tests for Participant-Level Missed Infusion Counts"
)
```

```{r participant-level-primary-model, message=FALSE}
# missed2plus = 1 if the participant had >=2 missed infusions, 0 otherwise.
# Secondary participant-level model:
# Logistic regression of having >=2 missed infusions (missed2plus)
# on age, sex, country, and treatment arm,
# adjusted for total_infusions (opportunity to miss visits).
missed_counts_primary <- infusions_only[
  ,
  .(
    missed = sum(missed_infusion_core, na.rm = TRUE),
    total_infusions = .N
  ),
  by = .(protocol, uid)
]
missed_counts_primary[, missed2plus := as.integer(missed >= 2)]

missed_counts_cov_primary <- merge(
  missed_counts_primary,
  subject_master[, .(protocol, uid, age, sex, country, rx_code)],
  by = c("protocol", "uid"),
  all.x = TRUE
)

logit_2plus_data <- na.omit(missed_counts_cov_primary[, .(
  missed2plus, age, sex, country, rx_code, total_infusions
)])

# Explicit reference categories for manuscript-consistent interpretation.
logit_2plus_data[, rx_code := stats::relevel(factor(rx_code), ref = "C3")]
country_ref <- if ("United States" %in% unique(logit_2plus_data$country)) {
  "United States"
} else {
  names(sort(table(logit_2plus_data$country), decreasing = TRUE))[1]
}
logit_2plus_data[, country := stats::relevel(factor(country), ref = country_ref)]
logit_2plus_data[, sex := factor(sex)]

logit_2plus <- glm(
  missed2plus ~ age + sex + country + rx_code + total_infusions,
  data = logit_2plus_data,
  family = binomial(),
  control = glm.control(maxit = 100)
)
logit_2plus_tidy <- tidy(logit_2plus, exponentiate = TRUE, conf.int = TRUE)

kable(
  logit_2plus_tidy[, c("term", "estimate", "conf.low", "conf.high", "p.value")],
  col.names = c("Variable", "Odds Ratio", "2.5% CI", "97.5% CI", "p-value"),
  digits = 3,
  caption = "Secondary Participant-Level Logistic Model: Odds Ratios for >=2 Missed Infusions"
)
```

```{r secondary-participant-age-prediction-plot, message=FALSE, fig.cap="Secondary participant-level model visualization: predicted probability of having >=2 missed infusions by age."}
# Secondary participant-level visualization:
# Predicted probability of having >=2 missed infusions by age
# from the participant-level logistic model (holding other covariates fixed).
age_min <- max(18, floor(min(logit_2plus_data$age, na.rm = TRUE)))
age_max <- min(50, ceiling(max(logit_2plus_data$age, na.rm = TRUE)))
age_seq <- seq(age_min, age_max, by = 1)

pred_df <- data.table(
  age = age_seq,
  sex = factor(levels(logit_2plus_data$sex)[1], levels = levels(logit_2plus_data$sex)),
  country = factor(country_ref, levels = levels(logit_2plus_data$country)),
  rx_code = factor("C3", levels = levels(logit_2plus_data$rx_code)),
  total_infusions = stats::median(logit_2plus_data$total_infusions, na.rm = TRUE)
)
pred_df[, pred_prob := as.numeric(stats::predict(logit_2plus, newdata = pred_df, type = "response"))]

ggplot(pred_df, aes(x = age, y = pred_prob)) +
  geom_line(linewidth = 1.2, color = "#E35D10") +
  labs(
    title = "Predicted probability of having >=2 missed infusions by age",
    x = "Age",
    y = "Predicted probability (>=2 missed infusions)"
  ) +
  theme_minimal()
```

# 4. Visit-Level Adherence (Per-Infusion Mixed-Effects Models)
<!-- This section fits per-infusion mixed-effects logistic regression models for missed infusion,
with participant-level random intercepts to account for repeated visits. -->

```{r logistic-regression-missed-infusion, message=FALSE}
logit_data <- infusions_only[
  !age_bin %in% c("<18", ">50") & !is.na(age_bin) & !is.na(sex) & !is.na(country) & !is.na(rx_code),
  .(
    missed = as.integer(missed_infusion_core),
    age_bin, sex, country, rx_code, infusion_num, participant_id
  )
]

logit_data[, age_bin := factor(as.character(age_bin), levels = c("18-25", "26-33", "34-41", "42-50"))]
logit_data[, rx_code := stats::relevel(factor(rx_code), ref = "C3")]
country_ref_visit <- if ("United States" %in% unique(logit_data$country)) {
  "United States"
} else {
  names(sort(table(logit_data$country), decreasing = TRUE))[1]
}
logit_data[, country := stats::relevel(factor(country), ref = country_ref_visit)]
logit_data[, sex := factor(sex)]
if ("Female" %in% levels(logit_data$sex)) {
  logit_data[, sex := stats::relevel(sex, ref = "Female")]
}
logit_data[, infusion_num_f := factor(infusion_num)]

# Visit-level mixed-effects model:
# Logistic regression for missed infusion at each scheduled infusion visit
# as a function of age group, sex, country, and treatment arm,
# adjusted for infusion number, with a random intercept for participant_id
# to account for repeated visits.
logit_model <- fit_mixed_logit(
  missed ~ age_bin + sex + country + rx_code + infusion_num_f + (1 | participant_id),
  data = logit_data
)
logit_tidy <- tidy_mixed_or(logit_model)

kable(logit_tidy[, .(term, estimate, conf.low, conf.high, p.value)],
      col.names = c("Variable", "Odds Ratio", "2.5% CI", "97.5% CI", "p-value"),
      digits = 3,
      caption = "Odds Ratios and Confidence Intervals for Predictors of Missed Infusions (Mixed-Effects Logistic Regression, Adjusted for Infusion Number)")
```

**Explanation:** Fits a mixed-effects logistic regression (participant random intercept) for missed visits using age band, sex, country, and treatment arm predictors; the table lists adjusted odds ratios.


```{r logistic-regression-forest-plot, message=FALSE}
# Forest plot of odds ratios from logistic regression
logit_forest <- logit_tidy[logit_tidy$term != "(Intercept)", ]

# Clean term labels for readability
clean_label <- function(x) {
  x <- gsub("^age_bin", "Age ", x)
  x <- gsub("^sex", "Sex: ", x)
  x <- gsub("^country", "Country: ", x)
  x <- gsub("^rx_code", "Treatment Arm: ", x)
  x <- gsub(":", " ", x)
  x
}

logit_forest$Label <- clean_label(logit_forest$term)
logit_forest$Label <- factor(logit_forest$Label, levels = rev(unique(logit_forest$Label)))

ggplot(logit_forest, aes(x = estimate, y = Label)) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "grey50") +
  geom_point(size = 3, color = "#0073C2FF") +
  geom_errorbar(aes(y = Label, xmin = conf.low, xmax = conf.high), orientation = "y", width = 0.2, color = "#0073C2FF") +
  scale_x_continuous(trans = "log10") +
  labs(
    title = "Odds Ratios for Predictors of Missed Infusions",
    x = "Odds Ratio (log scale)",
    y = NULL
  ) +
  theme_minimal()
```

**Explanation:** Converts the logistic regression output into a forest plot with log-scale odds ratios so you can visually compare point estimates and confidence intervals against the null (odds ratio = 1). 


```{r missed-infusion-by-arm-age-plot, message=FALSE}
missed_by_arm_age <- infusions_only[!age_bin %in% c("<18", ">50"), .(
  total = .N,
  missed = sum(missed_infusion_core == 1L, na.rm = TRUE),
  missed_rate = mean(missed_infusion_core == 1L, na.rm = TRUE)
), by = .(rx_code, age_bin)]

missed_by_arm_age[, `:=`(
  ci = mapply(function(miss, tot) binom.test(miss, tot)$conf.int[2], missed, total),
  ci_lower = mapply(function(miss, tot) binom.test(miss, tot)$conf.int[1], missed, total)
)]

missed_by_arm_age[, rx_code := factor(rx_code,
  levels = c("C3", "T1", "T2"),
  labels = c("Placebo", "Low-dose VRC01", "High-dose VRC01")
)]


p_missed_arm_age <- ggplot(missed_by_arm_age, aes(x = rx_code, y = missed_rate, fill = age_bin)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci), position = position_dodge(width = 0.8), width = 0.2) +
  scale_fill_manual(values = age_palette, breaks = names(age_palette)) +
  labs(title = "Proportion of Missed Infusions by Treatment Arm and Age Group",
       x = "Treatment Arm",
       y = "Missed Infusion Rate",
       fill = "Age Group") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_minimal()

print(p_missed_arm_age)


```

**Explanation:** Calculates missed counts, totals, and confidence intervals for every treatment arm × age band combination and plots them with error bars.


```{r missed-infusion-by-arm-age-table, message=FALSE}
# knitr loaded in setup
missed_by_arm_age_table <- missed_by_arm_age[order(rx_code, age_bin), .(Treatment_Arm = rx_code, Age_Group = age_bin, Missed_Infusions = missed, Total_Infusions = total, Missed_Rate = round(missed_rate, 3))]
kable(missed_by_arm_age_table, col.names = c("Treatment Arm", "Age Group", "Missed Infusions", "Total Infusions", "Missed Rate"), caption = "Missed Infusions by Treatment Arm and Age Group")
```

**Explanation:** Shows the numeric summary (missed, total, rate) for each arm × age band so you can reference the exact values from the plot.


```{r missed-infusion-by-pooled-arm-age, message=FALSE}
# ggplot2 loaded in setup
# knitr loaded in setup

# Pool T1 and T2 into one treatment group
infusions_only[, pooled_arm := ifelse(rx_code %in% c("T1", "T2"), "T1+T2", as.character(rx_code))]

# Summarize missed infusions by pooled treatment arm and age group (exclude <18 and >50)
missed_by_pooled_arm_age <- infusions_only[!age_bin %in% c("<18", ">50"), .(
  total = .N,
  missed = sum(missed_infusion_core == 1L, na.rm = TRUE),
  missed_rate = mean(missed_infusion_core == 1L, na.rm = TRUE)
), by = .(pooled_arm, age_bin)]

# Binomial confidence intervals
missed_by_pooled_arm_age[, ci := mapply(function(miss, tot) binom.test(miss, tot)$conf.int[2], missed, total)]
missed_by_pooled_arm_age[, ci_lower := mapply(function(miss, tot) binom.test(miss, tot)$conf.int[1], missed, total)]

# Plot
p_missed_pooled_arm_age <- ggplot(missed_by_pooled_arm_age, aes(x = pooled_arm, y = missed_rate, fill = age_bin)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci), position = position_dodge(width = 0.8), width = 0.2) +
  scale_fill_manual(values = age_palette, breaks = names(age_palette)) +
  labs(title = "Proportion of Missed Infusions by Pooled Treatment Arm and Age Group",
       x = "Pooled Treatment Arm",
       y = "Missed Infusion Rate",
       fill = "Age Group") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_minimal()
print(p_missed_pooled_arm_age)

# Table
missed_by_pooled_arm_age_table <- missed_by_pooled_arm_age[order(pooled_arm, age_bin), .(
  Pooled_Treatment_Arm = pooled_arm, Age_Group = age_bin, Missed_Infusions = missed, Total_Infusions = total, Missed_Rate = round(missed_rate, 3))]
kable(missed_by_pooled_arm_age_table, col.names = c("Pooled Treatment Arm", "Age Group", "Missed Infusions", "Total Infusions", "Missed Rate"), caption = "Missed Infusions by Pooled Treatment Arm and Age Group")
```

**Explanation:** Combines T1 and T2 into one pooled arm, then summarizes missed rates by pooled arm and age band to simplify the comparison with control.


```{r pooled-arm-compare, message=FALSE}
# Create a binary variable for pooled arm
infusions_only[, pooled_arm := ifelse(rx_code %in% c("T1", "T2"), "T1+T2", as.character(rx_code))]

# Filter to just T1+T2 and C3
compare_data <- infusions_only[pooled_arm %in% c("T1+T2", "C3") & !is.na(infusion_outcome)]

# Create a 2x2 table: missed vs not missed by group
compare_data[, missed := as.integer(missed_infusion_core)]
table_compare <- table(compare_data$pooled_arm, compare_data$missed)

# Run test
if (all(table_compare >= 5)) {
  test_result <- chisq.test(table_compare)
} else {
  test_result <- fisher.test(table_compare)
}

table_compare  # Show table
test_result    # Show test result
```

**Explanation:** Creates a 2×2 table comparing pooled treatment (T1+T2) versus control (C3) for missed vs completed infusions and runs the appropriate chi-squared or Fisher test.


```{r missed-infusion-by-pooled-arm-plot, message=FALSE}
# ggplot2 loaded in setup

# Summarize missed infusions by pooled arm
missed_by_pooled <- compare_data[, .(
  total = .N,
  missed = sum(missed, na.rm = TRUE),
  missed_rate = mean(missed, na.rm = TRUE)
), by = pooled_arm]

# Binomial confidence intervals
missed_by_pooled[, ci_lower := mapply(function(miss, tot) binom.test(miss, tot)$conf.int[1], missed, total)]
missed_by_pooled[, ci_upper := mapply(function(miss, tot) binom.test(miss, tot)$conf.int[2], missed, total)]

# Plot
ggplot(missed_by_pooled, aes(x = pooled_arm, y = missed_rate, fill = pooled_arm)) +
  geom_bar(stat = "identity", width = 0.6) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2) +
  geom_text(aes(label = paste0(round(missed_rate * 100, 2), "%"), y = missed_rate / 2), vjust = 0.5, size = 4) +
  labs(title = "Missed Infusion Rate by Treatment Group",
       x = "Treatment Group",
       y = "Missed Infusion Rate") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, max(missed_by_pooled$ci_upper) * 1.1)) +
  theme_minimal() +
  theme(legend.position = "none")
```

**Explanation:** Plots the missed-rate comparison between the pooled treatment group and control, with confidence intervals and percent labels.


# Statistical Test for Interaction

```{r logistic-regression-interaction, message=FALSE}
# Visit-level mixed-effects interaction model:
# Logistic regression for missed infusion at each scheduled infusion visit,
# with pooled treatment-by-age interaction and participant random intercept.
logit_interaction_data <- infusions_only[
  !age_bin %in% c("<18", ">50") & pooled_arm %in% c("T1+T2", "C3") &
    !is.na(age_bin) & !is.na(sex) & !is.na(country) & !is.na(pooled_arm),
  .(
    missed = as.integer(missed_infusion_core),
    age_bin, sex, country, pooled_arm, infusion_num, participant_id
  )
]

logit_interaction_data[, age_bin := factor(as.character(age_bin), levels = c("18-25", "26-33", "34-41", "42-50"))]
logit_interaction_data[, pooled_arm := stats::relevel(factor(pooled_arm), ref = "C3")]
country_ref_interaction <- if ("United States" %in% unique(logit_interaction_data$country)) {
  "United States"
} else {
  names(sort(table(logit_interaction_data$country), decreasing = TRUE))[1]
}
logit_interaction_data[, country := stats::relevel(factor(country), ref = country_ref_interaction)]
logit_interaction_data[, sex := factor(sex)]
if ("Female" %in% levels(logit_interaction_data$sex)) {
  logit_interaction_data[, sex := stats::relevel(sex, ref = "Female")]
}
logit_interaction_data[, infusion_num_f := factor(infusion_num)]

logit_interaction <- fit_mixed_logit(
  missed ~ pooled_arm * age_bin + sex + country + infusion_num_f + (1 | participant_id),
  data = logit_interaction_data
)
logit_interaction_tidy <- tidy_mixed_or(logit_interaction)

kable(logit_interaction_tidy[, .(term, estimate, conf.low, conf.high, p.value)],
      col.names = c("Variable", "Odds Ratio", "2.5% CI", "97.5% CI", "p-value"),
      digits = 3,
      caption = "Odds Ratios and Confidence Intervals for Predictors of Missed Infusions (Mixed-Effects Model with Interaction Term)")
```

**Explanation:** Runs a mixed-effects logistic regression with a pooled-treatment-by-age interaction, adjusting for sex and country and accounting for repeated visits within participants.


# 5. AE and Risk of Missing the Next Infusion (Mixed-Effects Model)
<!-- This section creates lagged AE exposure and models risk of missing the
next scheduled infusion visit using participant-level random intercepts. -->

## Relationship Between AEs and Adherence

```{r read-reacto, message=FALSE, eval=FALSE}
# EXPLORATORY: not part of the primary manuscript results.
# data.table loaded in setup
# Read adverse event data
dt_reacto <- fread(reacto_file)
# Check structure and preview
dim(dt_reacto)
str(dt_reacto)
head(dt_reacto)
```

**Explanation:** Reloads the adverse event file, prints its dimensions, structure, and first few rows as a quick data check.


# (Next step: Merge the adverse event summary data with the adherence data to analyze their relationship)

```{r summarize-ae, message=FALSE}
# Summarize by AE type and severity
ae_summary <- dt_reacto[, .(
  N = .N
), by = .(rgtype, rgparamc, rgsevmaxc)][order(rgtype, rgparamc, rgsevmaxc)]

# knitr loaded in setup
kable(ae_summary, col.names = c("AE Type", "AE Parameter", "Severity", "Count"),
      caption = "Summary of Adverse Events by Type, Parameter, and Severity")
```

**Explanation:** Counts how many adverse events you have for each type, parameter, and severity and prints the results as a table.


```{r ae-total-by-severity, message=FALSE}
# Total number of AEs in each severity category
ae_total_by_severity <- dt_reacto[, .N, by = rgsevmaxc][order(rgsevmaxc)]
kable(ae_total_by_severity, col.names = c("Severity", "Total AEs"), caption = "Total Number of Adverse Events by Severity Category")

# Number of unique participants with at least one AE of each severity
ae_participants_by_severity <- dt_reacto[, .(Unique_Participants = uniqueN(uid)), by = rgsevmaxc][order(rgsevmaxc)]
kable(ae_participants_by_severity, col.names = c("Severity", "Participants with ≥1 AE"), caption = "Number of Participants Experiencing at Least One AE by Severity Category")
```

**Explanation:** Counts total adverse events and the number of participants experiencing them for each severity level.


```{r ae-adherence-link, message=FALSE}
# 1. Flag infusion-window AEs (excluding 'None' and 'None or Not gradable')
ae_flag_raw <- unique(
  dt_reacto[
    !rgsevmaxc %in% c("None", "None or Not gradable"),
    .(AE_at_visit = 1L),
    by = .(protocol, uid, visitno)
  ]
)

# 2. Align AE visits to infusion visits.
# QC only: assess direct visitno overlap (not used for primary alignment).
direct_match_n <- nrow(merge(
  infusions_only[, .(protocol, uid, visitno)],
  ae_flag_raw[, .(protocol, uid, visitno)],
  by = c("protocol", "uid", "visitno"),
  all = FALSE
))

# Locked primary alignment method:
# retention.visitno and reacto.visitno are not synchronized in this public extract.
# Therefore, map AE visit order to infusion visit order within participant.
infusion_map <- unique(infusions_only[, .(protocol, uid, infusion_num)])
setorder(infusion_map, protocol, uid, infusion_num)
infusion_map[, infusion_seq := seq_len(.N), by = .(protocol, uid)]

ae_visit_map <- unique(dt_reacto[, .(protocol, uid, visitno)])
setorder(ae_visit_map, protocol, uid, visitno)
ae_visit_map[, ae_seq := seq_len(.N), by = .(protocol, uid)]

ae_to_infusion <- merge(
  ae_visit_map[, .(protocol, uid, visitno, ae_seq)],
  infusion_map[, .(protocol, uid, infusion_num, infusion_seq)],
  by.x = c("protocol", "uid", "ae_seq"),
  by.y = c("protocol", "uid", "infusion_seq"),
  all.x = TRUE
)

ae_flag <- merge(
  ae_flag_raw,
  ae_to_infusion[, .(protocol, uid, visitno, infusion_num)],
  by = c("protocol", "uid", "visitno"),
  all.x = TRUE
)[
  !is.na(infusion_num),
  .(AE_at_infusion = as.integer(any(AE_at_visit == 1L))),
  by = .(protocol, uid, infusion_num)
]

infusions_ae <- merge(
  infusions_only,
  ae_flag,
  by = c("protocol", "uid", "infusion_num"),
  all.x = TRUE
)
ae_alignment_method <- "Sequential within-participant mapping (AE visit order -> infusion order)"

infusions_ae[is.na(AE_at_infusion), AE_at_infusion := 0L]
infusions_ae[, AE_at_infusion := as.integer(AE_at_infusion)]

ae_alignment_qc <- data.table(
  Alignment_Method = ae_alignment_method,
  Direct_VisitNo_Matches = direct_match_n,
  Infusion_Rows = nrow(infusions_only),
  Infusion_Rows_With_AE = infusions_ae[AE_at_infusion == 1L, .N]
)
kable(ae_alignment_qc, caption = "QC: AE-to-Infusion Alignment")

# AE_at_infusion: indicator of a qualifying AE at the current infusion visit.
# AE_prior: AE_at_infusion lagged by one infusion for each participant.
# In infusions_ae_next, 'missed' indicates whether the NEXT infusion visit was missed.
# 3. Order data and create lagged AE variable (AE at prior infusion)
setorder(infusions_ae, protocol, uid, infusion_num)
infusions_ae[, AE_prior := shift(AE_at_infusion, n = 1, type = "lag"), by = .(protocol, uid)]

# 4. Calculate missed next infusion rate by AE status at prior infusion
infusions_ae_next <- infusions_ae[!is.na(AE_prior)]
infusions_ae_next[, missed := as.integer(missed_infusion_core == 1L)]
missed_rate_by_ae <- infusions_ae_next[, .(
  N = .N,
  Missed_Next_Infusion = sum(missed),
  Missed_Rate = mean(missed)
), by = AE_prior]

kable(
  infusions_ae_next[, .N, by = AE_prior],
  col.names = c("AE Prior", "Rows"),
  caption = "Distribution Check: AE_prior"
)
kable(missed_rate_by_ae, col.names = c("AE at Prior Infusion", "N", "Missed Next Infusion", "Missed Rate"),
      caption = "Probability of Missing Next Infusion by AE Status at Prior Infusion")

# 5. Mixed-effects logistic regression: Predict missing next infusion
logit_ae_data <- infusions_ae_next[
  !age_bin %in% c("<18", ">50") & !is.na(age_bin) & !is.na(sex) & !is.na(country) & !is.na(rx_code),
  .(missed, AE_prior = as.integer(AE_prior), age_bin, sex, country, rx_code, infusion_num, participant_id)
]
if (uniqueN(logit_ae_data$AE_prior) < 2) {
  stop("AE_prior has no variation after alignment. Check AE-to-infusion mapping before interpreting AE model results.")
}
logit_ae_data[, age_bin := factor(as.character(age_bin), levels = c("18-25", "26-33", "34-41", "42-50"))]
logit_ae_data[, rx_code := stats::relevel(factor(rx_code), ref = "C3")]
country_ref_ae <- if ("United States" %in% unique(logit_ae_data$country)) {
  "United States"
} else {
  names(sort(table(logit_ae_data$country), decreasing = TRUE))[1]
}
logit_ae_data[, country := stats::relevel(factor(country), ref = country_ref_ae)]
logit_ae_data[, sex := factor(sex)]
if ("Female" %in% levels(logit_ae_data$sex)) {
  logit_ae_data[, sex := stats::relevel(sex, ref = "Female")]
}
logit_ae_data[, infusion_num_f := factor(infusion_num)]
# Visit-level secondary model:
# Mixed-effects logistic regression predicting risk of missing the next infusion visit,
# as a function of AE at the prior infusion (AE_prior), age group, sex, country, and treatment arm,
# adjusted for infusion number, with a random intercept for participant_id.
logit_ae_model <- fit_mixed_logit(
  missed ~ AE_prior + age_bin + sex + country + rx_code + infusion_num_f + (1 | participant_id),
  data = logit_ae_data
)
logit_ae_tidy <- tidy_mixed_or(logit_ae_model)
kable(logit_ae_tidy[, .(term, estimate, conf.low, conf.high, p.value)],
      col.names = c("Variable", "Odds Ratio", "2.5% CI", "97.5% CI", "p-value"),
      digits = 3,
      caption = "Odds Ratios for Predicting Missed Next Infusion (Mixed-Effects Model; Key Predictor: AE at Prior Infusion; Adjusted for Infusion Number)")
```

**Explanation:** Flags which infusions had recent AEs, merges that flag into the infusion dataset, and checks whether having an AE at the prior visit increases the chance of missing the next infusion (including a regression model).


```{r univariate-multivariate-logit, message=FALSE}
analysis_predictors <- c("age_bin", "country", "rx_code", "AE_prior", "infusion_num_f")
analysis_data <- as.data.table(logit_ae_data)
analysis_data <- analysis_data[complete.cases(analysis_data[, c("missed", analysis_predictors, "participant_id"), with = FALSE])]

run_univariate <- function(var) {
  form <- as.formula(paste0("missed ~ ", var, " + (1 | participant_id)"))
  out <- tidy_mixed_or(fit_mixed_logit(form, analysis_data))
  out[, Model := "Univariate"]
  out
}

univariate_results <- rbindlist(lapply(analysis_predictors, run_univariate), fill = TRUE)

multivariate_model <- fit_mixed_logit(
  missed ~ age_bin + country + rx_code + AE_prior + infusion_num_f + (1 | participant_id),
  data = analysis_data
)
multivariate_results <- tidy_mixed_or(multivariate_model)
multivariate_results[, Model := "Multivariate"]

logit_summary <- rbindlist(list(univariate_results, multivariate_results), fill = TRUE)[
  term != "(Intercept)",
  .(
    Model,
    Term = term,
    `Odds Ratio` = round(estimate, 3),
    `CI Low` = round(conf.low, 3),
    `CI High` = round(conf.high, 3),
    `p-value` = signif(p.value, 3)
  )
]

kable(logit_summary, caption = "Univariate and Multivariate Odds Ratios for Missed Infusion (Mixed-Effects Models)")
```

**Explanation:** Runs separate one-variable mixed-effects models and one combined mixed-effects model for age band, country, treatment arm, and prior AE, then reports adjusted odds ratios.


```{r total-ae-missed-by-arm, message=FALSE}
# Exclude pooled systemic symptoms and non-gradable AEs
ae_filtered <- dt_reacto[!rgparamc %in% c("Systemic Symptoms") & !rgsevmaxc %in% c("None", "None or Not gradable")]

# Total AEs by treatment arm (merge with subject_master for rx_code)
ae_by_arm <- merge(ae_filtered, subject_master[, .(protocol, uid, rx_code)], by = c("protocol", "uid"), all.x = TRUE)
total_aes_by_arm <- ae_by_arm[, .N, by = rx_code][order(rx_code)]

# Total missed infusions by treatment arm
missed_infusions_by_arm <- infusions_only[missed_infusion_core == 1L, .N, by = rx_code][order(rx_code)]

# Combine into one table
summary_by_arm <- merge(total_aes_by_arm, missed_infusions_by_arm, by = "rx_code", all = TRUE)
colnames(summary_by_arm) <- c("Treatment Arm", "Total AEs (non-None, non-Systemic)", "Total Missed Infusions")

# knitr loaded in setup
kable(summary_by_arm, caption = "Total Adverse Events and Missed Infusions by Treatment Arm")
```

**Explanation:** Totals the number of AEs (excluding non-gradable/systemic) and the number of missed infusions per treatment arm and shows them side-by-side.


```{r ae-missed-by-arm-infusion, message=FALSE}
# Total AEs by treatment arm and infusion number
ae_by_arm_infusion <- merge(ae_filtered, subject_master[, .(protocol, uid, rx_code)], by = c("protocol", "uid"), all.x = TRUE)
ae_by_arm_infusion <- ae_by_arm_infusion[, .N, by = .(rx_code, visitno)][order(rx_code, visitno)]
colnames(ae_by_arm_infusion) <- c("Treatment Arm", "Infusion Number", "Total AEs")

# Total missed infusions by treatment arm and infusion number
missed_by_arm_infusion <- infusions_only[missed_infusion_core == 1L, .N, by = .(rx_code, visitno)][order(rx_code, visitno)]
colnames(missed_by_arm_infusion) <- c("Treatment Arm", "Infusion Number", "Total Missed Infusions")

# Merge for plotting
summary_by_arm_infusion <- merge(ae_by_arm_infusion, missed_by_arm_infusion, by = c("Treatment Arm", "Infusion Number"), all = TRUE)

# knitr loaded in setup
kable(summary_by_arm_infusion, caption = "Total AEs and Missed Infusions by Treatment Arm and Infusion Number")

# Plot
# ggplot2 loaded in setup
# reshape2 loaded in setup
summary_long <- melt(summary_by_arm_infusion, id.vars = c("Treatment Arm", "Infusion Number"), variable.name = "Type", value.name = "Count")
summary_long <- summary_long[!is.na(summary_long$Count), ]

p <- ggplot(summary_long, aes(x = as.factor(`Infusion Number`), y = Count, fill = Type)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8)) +
  facet_wrap(~`Treatment Arm`, ncol = 1) +
  labs(title = "AEs and Missed Infusions by Treatment Arm and Infusion Number",
       x = "Infusion Number",
       y = "Count",
       fill = "Type") +
  theme_minimal()
print(p)
```

**Explanation:** For each treatment arm and infusion number, counts AEs and missed infusions, displays the table, and plots both metrics so you can see how they change over time.


```{r ae-missed-c3, message=FALSE}
c3_data <- summary_long[summary_long$`Treatment Arm` == "C3", ]
ggplot(c3_data, aes(x = as.factor(`Infusion Number`), y = Count, fill = Type)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8)) +
  labs(title = "AEs and Missed Infusions: C3",
       x = "Infusion Number",
       y = "Count",
       fill = "Type") +
  theme_minimal()
```

**Explanation:** Zooms in on the control arm (C3) and plots its AE counts versus missed infusions by infusion number.


```{r ae-missed-t1, message=FALSE}
t1_data <- summary_long[summary_long$`Treatment Arm` == "T1", ]
ggplot(t1_data, aes(x = as.factor(`Infusion Number`), y = Count, fill = Type)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8)) +
  labs(title = "AEs and Missed Infusions: T1",
       x = "Infusion Number",
       y = "Count",
       fill = "Type") +
  theme_minimal()
```

**Explanation:** Plots AE counts versus missed infusions over time for treatment arm T1.


```{r ae-missed-t2, message=FALSE}
t2_data <- summary_long[summary_long$`Treatment Arm` == "T2", ]
ggplot(t2_data, aes(x = as.factor(`Infusion Number`), y = Count, fill = Type)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8)) +
  labs(title = "AEs and Missed Infusions: T2",
       x = "Infusion Number",
       y = "Count",
       fill = "Type") +
  theme_minimal()
```

**Explanation:** Plots AE counts versus missed infusions over time for treatment arm T2.


```{r ae-missed-correlation, message=FALSE}
# Total AEs per participant (excluding 'None', 'None or Not gradable', and 'Systemic Symptoms')
ae_per_participant <- ae_filtered[, .N, by = .(protocol, uid)]
colnames(ae_per_participant)[3] <- "Total_AEs"

# Total missed infusions per participant
missed_per_participant <- infusions_only[missed_infusion_core == 1L, .N, by = .(protocol, uid)]
colnames(missed_per_participant)[3] <- "Total_Missed_Infusions"

# Merge
ae_missed_merged <- merge(ae_per_participant, missed_per_participant, by = c("protocol", "uid"), all = TRUE)
ae_missed_merged[is.na(Total_AEs), Total_AEs := 0]
ae_missed_merged[is.na(Total_Missed_Infusions), Total_Missed_Infusions := 0]

# Calculate correlation
cor_result <- cor(ae_missed_merged$Total_AEs, ae_missed_merged$Total_Missed_Infusions, method = "spearman")
cor_result

# Visualize
# ggplot2 loaded in setup
ggplot(ae_missed_merged, aes(x = Total_AEs, y = Total_Missed_Infusions)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(title = "Correlation Between Total AEs and Missed Infusions per Participant",
       x = "Total AEs (non-None, non-Systemic)",
       y = "Total Missed Infusions") +
  theme_minimal()
```

**Explanation:** Creates per-participant totals for AEs and missed infusions, joins them together, calculates a Spearman correlation, and shows a scatterplot with a trend line.


```{r ae-missed-correlation-by-arm, message=FALSE}
# Merge treatment arm into the per-participant summary
ae_missed_merged_arm <- merge(ae_missed_merged, subject_master[, .(protocol, uid, rx_code)], by = c("protocol", "uid"), all.x = TRUE)

# Calculate correlation for each treatment arm
cor_by_arm <- ae_missed_merged_arm[, .(
  Spearman_rho = cor(Total_AEs, Total_Missed_Infusions, method = "spearman")
), by = rx_code]
# knitr loaded in setup
kable(cor_by_arm, col.names = c("Treatment Arm", "Spearman's rho"), digits = 3, caption = "Correlation Between Total AEs and Missed Infusions by Treatment Arm")

# Faceted scatter plot
# ggplot2 loaded in setup
ggplot(ae_missed_merged_arm, aes(x = Total_AEs, y = Total_Missed_Infusions)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  facet_wrap(~rx_code) +
  labs(title = "Correlation Between Total AEs and Missed Infusions by Treatment Arm",
       x = "Total AEs (non-None, non-Systemic)",
       y = "Total Missed Infusions") +
  theme_minimal()
```

**Explanation:** Adds treatment arm labels to the per-participant totals, reports the correlation within each arm, and draws separate scatterplots for each arm.


```{r ae-missed-correlation-by-arm-age, message=FALSE}
# Merge age group into the per-participant summary
ae_missed_merged_arm_age <- merge(
  ae_missed_merged_arm, 
  subject_master[, .(protocol, uid, age_bin)], 
  by = c("protocol", "uid"), 
  all.x = TRUE
)

# Calculate correlation for each treatment arm and age group
cor_by_arm_age <- ae_missed_merged_arm_age[
  !is.na(age_bin) & !age_bin %in% c("<18", ">50"),
  .(Spearman_rho = cor(Total_AEs, Total_Missed_Infusions, method = "spearman")),
  by = .(rx_code, age_bin)
]
# knitr loaded in setup
kable(
  cor_by_arm_age, 
  col.names = c("Treatment Arm", "Age Group", "Spearman's rho"), 
  digits = 3, 
  caption = "Correlation Between Total AEs and Missed Infusions by Treatment Arm and Age Group"
)

# Faceted scatter plot
# ggplot2 loaded in setup
ggplot(
  ae_missed_merged_arm_age[!is.na(age_bin) & !age_bin %in% c("<18", ">50")],
  aes(x = Total_AEs, y = Total_Missed_Infusions)
) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  facet_grid(age_bin ~ rx_code) +
  labs(
    title = "Correlation Between Total AEs and Missed Infusions by Treatment Arm and Age Group",
    x = "Total AEs (non-None, non-Systemic)",
    y = "Total Missed Infusions"
  ) +
  theme_minimal()
```

**Explanation:** Adds age bands as well, reports correlations for every arm × age band, and draws faceted scatterplots to see how the relationship changes across groups.


```{r missed-infusions-proportion-by-arm-age-tidy, message=FALSE}
# dplyr loaded in setup
# purrr loaded in setup
# ggplot2 loaded in setup
# broom loaded in setup

# Prepare data: create a binary missed variable
data_for_analysis <- infusions_only %>%
  filter(!is.na(age_bin), !age_bin %in% c("<18", ">50")) %>%
  mutate(missed = missed_infusion_core == 1L)

# Summarise by treatment arm and age group
missed_by_arm_age_ci <- data_for_analysis %>%
  group_by(rx_code, age_bin) %>%
  summarise(
    missed = sum(missed, na.rm = TRUE),
    total = n(),
    prop_missed = missed / total,
    .groups = "drop"
  ) %>%
  mutate(
    # Wilson score CI for binomial proportion
    ci = map2(missed, total, ~ binom.test(.x, .y)$conf.int),
    ci_low = map_dbl(ci, 1),
    ci_high = map_dbl(ci, 2)
  )

# Plot without percent labels
p <- ggplot(missed_by_arm_age_ci, aes(x = age_bin, y = prop_missed, fill = rx_code)) +
  geom_col(position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high),
                position = position_dodge(width = 0.9), width = 0.2) +
  labs(title = "Proportion of Missed Infusions by Treatment Arm and Age Group",
       x = "Age Group", y = "Proportion Missed", fill = "Treatment Arm") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_minimal()
print(p)

# Table of percentages and CIs
# knitr loaded in setup
missed_table <- missed_by_arm_age_ci %>%
  mutate(
    Percent_Missed = round(100 * prop_missed, 2),
    CI_Low = round(100 * ci_low, 2),
    CI_High = round(100 * ci_high, 2)
  ) %>%
  dplyr::select(rx_code, age_bin, Percent_Missed, CI_Low, CI_High)

kable(
  missed_table,
  col.names = c("Treatment Arm", "Age Group", "% Missed", "CI Low", "CI High"),
  caption = "Proportion of Missed Infusions by Treatment Arm and Age Group (with 95% CI)"
)
```

**Explanation:** Uses tidyverse tools to compute missed percentages plus confidence intervals for each arm × age band, plots them without labels, and provides a formatted table of the percentages.


```{r missed-infusions-proportion-by-arm-age-labels, message=FALSE, eval=FALSE}
# Plot with percent labels above bars
p <- ggplot(missed_by_arm_age_ci, aes(x = age_bin, y = prop_missed, fill = rx_code)) +
  geom_col(position = position_dodge(width = 0.9)) +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high),
                position = position_dodge(width = 0.9), width = 0.2) +
  geom_text(
    aes(label = paste0(round(100 * prop_missed, 2), "%")),
    position = position_dodge(width = 0.9),
    vjust = -0.5, size = 4
  ) +
  labs(title = "Proportion of Missed Infusions by Treatment Arm and Age Group",
       x = "Age Group", y = "Proportion Missed", fill = "Treatment Arm") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = expansion(mult = c(0, 0.12))) +
  theme_minimal()
print(p)
```

**Explanation:** Plots the same arm × age band missed percentages but adds percentage labels above each bar for easier reading.



```{r missed-infusions-by-arm-age, message=FALSE}
missed_by_arm_age <- infusions_only[missed_infusion_core == 1L & !is.na(age_bin) & !age_bin %in% c("<18", ">50"),
  .N, by = .(rx_code, age_bin)][order(rx_code, age_bin)]
# knitr loaded in setup
kable(missed_by_arm_age, col.names = c("Treatment Arm", "Age Group", "Missed Infusions"), caption = "Number of Missed Infusions by Treatment Arm and Age Group")
```

**Explanation:** Shows the raw number of missed infusions for each arm × age band combination (excluding the youngest and oldest groups).

# 6. Secondary / Exploratory Analyses
<!-- EXPLORATORY: not part of the primary manuscript results. -->


```{r scratch-26-33-tests, message=FALSE, eval=FALSE}
subset_26_33 <- data_for_analysis %>%
  filter(age_bin == "26-33")

table_26_33 <- table(subset_26_33$missed, subset_26_33$rx_code)

  chisq.test(table_26_33)
  
    fisher.test(table_26_33)
```

**Explanation:** (Legacy scratch chunk) Demonstrates how to run chi-squared and Fisher tests on the 26–33 age band using the tidyverse pipeline; kept for reference even though the next chunk repeats the test more cleanly.



```{r missed-infusions-stat-test-26-33, message=FALSE, warning=FALSE}
# Subset to 26-33 age group
subset_26_33 <- infusions_only[age_bin == "26-33"]

# Descriptive cross-tab (participant-level, independent rows):
# any missed infusion (yes/no) by treatment arm within age 26-33.
subset_26_33_participant <- subset_26_33[
  ,
  .(any_missed = as.integer(any(missed_infusion_core == 1L, na.rm = TRUE))),
  by = .(protocol, uid, rx_code)
]
tab_26_33 <- table(subset_26_33_participant$rx_code, subset_26_33_participant$any_missed)

# Run test
if (all(tab_26_33 >= 5)) {
  test_26_33 <- chisq.test(tab_26_33)
} else {
  test_26_33 <- fisher.test(tab_26_33)
}

tab_26_33
print(test_26_33)

# Mixed-effects logistic regression for 26-33 group (visit-level repeated measures)
# Visit-level mixed-effects subgroup model:
# Estimates treatment-arm differences in missed infusion within the 26-33 age stratum,
# with participant random intercepts for repeated visits.
subset_26_33[, missed := as.integer(missed_infusion_core)]
subset_26_33[, participant_id := interaction(protocol, uid, drop = TRUE)]
logit_26_33 <- fit_mixed_logit(missed ~ rx_code + (1 | participant_id), data = subset_26_33)
logit_26_33_tidy <- tidy_mixed_or(logit_26_33)
logit_26_33_tidy
```

**Explanation:** Formally runs the contingency test (chi-squared or Fisher) for the 26–33 age band and adds a simple logistic regression so you know whether treatment arm matters in that slice.


```{r ae-by-arm-age, message=FALSE}
# Guard for out-of-order chunk execution in RStudio
if (!exists("ae_filtered")) {
  ae_filtered <- dt_reacto[
    !rgparamc %in% c("Systemic Symptoms") &
      !rgsevmaxc %in% c("None", "None or Not gradable")
  ]
}
if (!"age_bin" %in% names(subject_master)) {
  subject_master[, age_bin := cut(
    age,
    breaks = age_bin_breaks,
    labels = age_bin_levels,
    right = FALSE,
    include.lowest = TRUE,
    ordered_result = TRUE
  )]
}

# Merge rx_code and age_bin into ae_filtered
ae_with_arm <- merge(
  ae_filtered,
  subject_master[, .(protocol, uid, rx_code, age_bin)],
  by = c("protocol", "uid"),
  all.x = TRUE
)

# Now summarize
ae_by_arm_age <- ae_with_arm[
  !is.na(uid), 
  .N, 
  by = .(rx_code, age_bin)
][order(rx_code, age_bin)]
# knitr loaded in setup
kable(ae_by_arm_age, col.names = c("Treatment Arm", "Age Group", "Total AEs"), caption = "Total AEs by Treatment Arm and Age Group")
```

**Explanation:** Counts how many adverse events occurred in each treatment arm × age band combination and prints the results.


```{r total-unique-participants, message=FALSE}
# Total number of unique participants (unique protocol/uid)
n_participants <- uniqueN(infusions_only[, .(protocol, uid)])
n_participants
```

**Explanation:** Counts how many unique participants appear in the infusion dataset so you know the study sample size for this analysis.


```{r total-retention-rate, message=FALSE}
# Find the highest infusion number (final visit)
final_infusion <- max(infusions_only$infusion_num, na.rm = TRUE)

# Number of participants who attended and were infused at the final visit
retained_participants <- uniqueN(
  infusions_only[infusion_num == final_infusion & infusion_outcome == "Arrived + Infused", .(protocol, uid)]
)

# Total number of unique participants
total_participants <- uniqueN(infusions_only[, .(protocol, uid)])

# Retention rate
retention_rate <- retained_participants / total_participants
retention_rate
```

**Explanation:** Calculates the proportion of participants who made it to the final infusion and were infused, which serves as the overall retention rate.


```{r anova-age-by-arm, message=FALSE}
# ANOVA: Age by Treatment Arm
anova_age <- aov(age ~ rx_code, data = subject_master)
summary(anova_age)
# Optionally, Tukey post-hoc test
TukeyHSD(anova_age)
```

**Explanation:** Runs an ANOVA (and optional Tukey post-hoc test) to see if mean age differs between treatment arms.


```{r kruskal-ae-missed-by-arm, message=FALSE}
# Kruskal-Wallis test for total AEs by treatment arm
kruskal_ae <- kruskal.test(Total_AEs ~ rx_code, data = ae_missed_merged_arm)
kruskal_ae

# Kruskal-Wallis test for total missed infusions by treatment arm
kruskal_missed <- kruskal.test(Total_Missed_Infusions ~ rx_code, data = ae_missed_merged_arm)
kruskal_missed
```

**Explanation:** Uses the non-parametric Kruskal-Wallis test to compare total AE counts and total missed infusions across treatment arms.


```{r km-logrank-missed, message=FALSE, eval=FALSE}
library(survival)
library(survminer)
# Placeholder: Time to second missed infusion by treatment arm
# You need a data.frame 'time_to_event' with columns: time, event (1=second missed, 0=censored), rx_code
# Example code:
# km_fit <- survfit(Surv(time, event) ~ rx_code, data = time_to_event)
# ggsurvplot(km_fit, data = time_to_event, pval = TRUE, risk.table = TRUE)
# survdiff(Surv(time, event) ~ rx_code, data = time_to_event)
```

**Explanation:** Provides template code for a Kaplan-Meier/time-to-event analysis of time until the second missed infusion; it is a placeholder for when that dataset becomes available.


```{r logistic-2plus-missed, message=FALSE, warning=FALSE, eval=FALSE}
# Create binary outcome: 1 if 2+ missed, 0 otherwise
missed_counts[, missed2plus := as.integer(missed >= 2)]
missed_counts[, total_infusions := .N, by = .(protocol, uid)]

# Merge in participant-level covariates (reduced set to avoid sparse separation)
missed_counts_cov <- merge(
  missed_counts,
  subject_master[, .(protocol, uid, age, sex, country, rx_code)],
  by = c("protocol", "uid"),
  all.x = TRUE
)

logit_2plus_data <- na.omit(missed_counts_cov[, .(missed2plus, age, sex, country, rx_code, total_infusions)])
logit_2plus <- glm(
  missed2plus ~ age + sex + country + rx_code + total_infusions,
  data = logit_2plus_data,
  family = binomial(),
  control = glm.control(maxit = 100)
)
logit_2plus_tidy <- tidy(logit_2plus, exponentiate = TRUE, conf.int = TRUE)

kable(logit_2plus_tidy[, c("term", "estimate", "conf.low", "conf.high", "p.value")],
      col.names = c("Variable", "Odds Ratio", "2.5% CI", "97.5% CI", "p-value"),
      digits = 3,
      caption = "Odds Ratios for Predicting 2+ Missed Infusions (Participant-Level)")
```

**Explanation:** Builds a participant-level dataset, labels anyone with 2+ missed infusions, and runs a logistic regression to see which demographics or arms predict that outcome.



```{r pearson-correlation-ae-missed, message=FALSE}
# Pearson correlation
cor_pearson <- cor(ae_missed_merged$Total_AEs, ae_missed_merged$Total_Missed_Infusions, method = "pearson")
cor_pearson
```

**Explanation:** Computes the Pearson correlation between total AEs and total missed infusions using the per-participant summary created earlier.


```{r pooled-local-symptom-heatmap-long, message=FALSE, warning=FALSE}
# Define local symptoms
local_symptoms <- c("Erythema", "Erythema and/or Induration", "Induration", "Pain", "Pain and/or Tenderness", "Tenderness")

# Pool local symptoms: for each participant/visit, did ANY local symptom occur?
local_any <- dt_reacto %>%
  filter(rgparamc %in% local_symptoms, rgsevmax > 0) %>%
  group_by(protocol, uid, visitno) %>%
  summarise(Local_Symptoms = as.integer(any(rgsevmax > 0)), .groups = "drop") %>%
  filter(Local_Symptoms == 1) %>%
  mutate(rgtype = "local", rgparamc = "Local Symptoms")

# Individual symptoms (as before)
symptom_by_visit <- dt_reacto %>%
  filter(rgsevmax > 0) %>%
  group_by(visitno, rgtype, rgparamc) %>%
  summarise(n = n(), .groups = "drop")

# Add pooled local symptoms to the summary
local_symptom_counts <- local_any %>%
  group_by(visitno, rgtype, rgparamc) %>%
  summarise(n = n(), .groups = "drop")

symptom_by_visit_type_pooled <- bind_rows(symptom_by_visit, local_symptom_counts)

# Percent of participants with each symptom at each visit
n_participants <- dt_reacto %>%
  group_by(visitno) %>%
  summarise(n_uid = n_distinct(uid), .groups = "drop")

symptom_by_visit_type_pooled <- symptom_by_visit_type_pooled %>%
  left_join(n_participants, by = "visitno") %>%
  mutate(percent = 100 * n / n_uid)

# Order symptoms: pooled at top, then by frequency
symptom_order <- symptom_by_visit_type_pooled %>%
  group_by(rgtype, rgparamc) %>%
  summarise(total_n = sum(n), .groups = "drop") %>%
  arrange(rgtype, desc(total_n)) %>%
  group_by(rgtype) %>%
  mutate(order = ifelse(rgtype == "local" & rgparamc == "Local Symptoms", 0, row_number()))

symptom_by_visit_type_pooled <- symptom_by_visit_type_pooled %>%
  left_join(symptom_order %>% dplyr::select(rgtype, rgparamc, order), by = c("rgtype", "rgparamc")) %>%
  mutate(rgparamc = reorder(rgparamc, -order))

# Plot
# ggplot2 loaded in setup
ggplot(symptom_by_visit_type_pooled, aes(x = factor(visitno), y = rgparamc, fill = percent)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(option = "C") +
  facet_wrap(~ rgtype, ncol = 1, scales = "free_y") +
  labs(
    title = "Symptom Frequency by Visit Number and AE Type",
    x = "Visit Number",
    y = "Symptom (sorted by overall frequency)",
    fill = "Percent of Participants"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

**Explanation:** Pools together local reactogenicity symptoms, calculates how common each symptom is at each visit, and draws a heat map (plus supporting tables) to visualize symptom frequencies over time.


```{r infusion-outcome-proportions, message=FALSE}
# Proportion of each infusion outcome
outcome_props <- infusions_only[, .N, by = infusion_outcome][
  , prop := 100 * N / sum(N)]
outcome_props
```

**Explanation:** Calculates the percentage of visits that fall into each infusion outcome category (infused, arrived not infused, missed).


```{r missed-infusion-rate-barplot-percentage, message=FALSE}
# ggplot2 loaded in setup

# Bar plot of missed infusion rate by infusion number, with percent labels above bars
ggplot(missed_by_infusion, aes(x = factor(infusion_num), y = missed_pct)) +
  geom_bar(stat = "identity", fill = "#0073C2FF", width = 0.7) +
  geom_text(aes(label = paste0(round(100 * missed_pct, 2), "%")), 
            vjust = -0.3, size = 4) +
  labs(title = "Missed Infusion Rate by Infusion Number (Percent Labels)",
       x = "Infusion Number",
       y = "Missed Infusion Rate") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_minimal()
```

**Explanation:** Recreates the missed-rate-by-infusion bar chart but labels each bar with the percentage for presentations.


```{r missed-infusion-rate-barplot-combined, message=FALSE}
# ggplot2 loaded in setup

ggplot(missed_by_infusion, aes(x = factor(infusion_num), y = missed_pct)) +
  geom_bar(stat = "identity", fill = "#0073C2FF", width = 0.7) +
  # Count label (slightly above the bar)
  geom_text(aes(label = missed), vjust = -0.3, size = 4) +
  # Percent label (further above the bar)
  geom_text(aes(label = paste0(round(100 * missed_pct, 2), "%")), 
            vjust = -1.2, size = 4, color = "black") +
  labs(title = "Missed Infusion Rate by Infusion Number (Count and Percent Labels)",
       x = "Infusion Number",
       y = "Missed Infusion Rate") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme_minimal()
```

**Explanation:** Produces a combined bar chart that shows both the percentage missed and the raw counts at each infusion number for quick comparison.


```{r missed-infusion-rate-by-arm, message=FALSE}
# dplyr loaded in setup
# ggplot2 loaded in setup
# purrr loaded in setup

# Summarize missed infusions by treatment arm
missed_by_arm <- infusions_only %>%
  filter(!is.na(rx_code)) %>%
  group_by(rx_code) %>%
  summarise(
    missed = sum(missed_infusion_core == 1L, na.rm = TRUE),
    total = n(),
    missed_rate = missed / total
  ) %>%
  mutate(
    # Binomial 95% CI
    ci = map2(missed, total, ~ binom.test(.x, .y)$conf.int),
    ci_low = map_dbl(ci, 1),
    ci_high = map_dbl(ci, 2)
  )

# Plot
ggplot(missed_by_arm, aes(x = rx_code, y = missed_rate, fill = rx_code)) +
  geom_col(width = 0.7) +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.2) +
  geom_text(aes(label = missed), vjust = -0.5, size = 5) +
  labs(
    title = "Missed Infusion Rate by Treatment Arm",
    x = "Treatment Arm",
    y = "Missed Infusion Rate",
    fill = "Treatment Arm",
    caption = "Number above each bar = total n (missed infusions)"
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, max(missed_by_arm$ci_high) * 1.1)) +
  theme_minimal() +
  theme(legend.position = "none")
```

**Explanation:** Summarizes missed counts for each treatment arm, adds confidence intervals, and plots the missed rates side-by-side.


```{r missed-infusion-rate-by-protocol, message=FALSE}
# dplyr loaded in setup
# ggplot2 loaded in setup
# purrr loaded in setup

# Summarize missed infusions by protocol
missed_by_protocol <- infusions_only %>%
  filter(!is.na(protocol)) %>%
  group_by(protocol) %>%
  summarise(
    missed = sum(missed_infusion_core == 1L, na.rm = TRUE),
    total = n(),
    missed_rate = missed / total
  ) %>%
  mutate(
    # Binomial 95% CI
    ci = map2(missed, total, ~ binom.test(.x, .y)$conf.int),
    ci_low = map_dbl(ci, 1),
    ci_high = map_dbl(ci, 2)
  )

# Plot
ggplot(missed_by_protocol, aes(x = protocol, y = missed_rate, fill = protocol)) +
  geom_col(width = 0.7) +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.2) +
  geom_text(aes(label = missed), vjust = 8.0, size = 5) +
  labs(
    title = "Missed Infusion Rate by Protocol",
    x = "Protocol",
    y = "Missed Infusion Rate",
    fill = "Protocol",
    caption = "Number above each bar = total n (missed infusions)"
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), limits = c(0, max(missed_by_protocol$ci_high) * 1.1)) +
  theme_minimal() +
  theme(legend.position = "none")
```

**Explanation:** Does the same as above but groups by clinical protocol instead of treatment arm.


```{r n-participants-no-missed-infusions, message=FALSE}
# Number of participants with zero missed infusions
missed_counts <- infusions_only[, .(missed = sum(missed_infusion_core == 1L, na.rm = TRUE)), by = .(protocol, uid)]
n_no_missed <- missed_counts[missed == 0, .N]
n_no_missed
```

**Explanation:** Counts how many participants never missed an infusion, which is another simple retention metric.


```{r table1-baseline-demographics, message=FALSE, eval=FALSE}
# tableone loaded in setup
# knitr loaded in setup

# Variables to include in Table 1
table1_vars <- c("age", "sex", "race", "ethnicity", "country", "rx_code", "protocol")

# Table 1 for all participants
baseline_table1 <- CreateTableOne(vars = table1_vars, data = subject_master)
kable(print(baseline_table1, showAllLevels = TRUE), caption = "Baseline Demographics and Study Characteristics (All Participants)")

# Table 1 stratified by treatment arm
baseline_table1_by_arm <- CreateTableOne(vars = table1_vars, strata = "rx_code", data = subject_master)
kable(print(baseline_table1_by_arm, showAllLevels = TRUE), caption = "Baseline Demographics and Study Characteristics by Treatment Arm")
```

**Explanation:** Generates classic Table 1 outputs (overall and stratified by arm) using CreateTableOne so you can report baseline demographics.


```{r custom-adherence-summary, message=FALSE, eval=FALSE}
# dplyr loaded in setup
# tidyr loaded in setup
# knitr loaded in setup

# Prepare missed_counts with adherence categories
missed_counts <- infusions_only[, .(missed = sum(missed_infusion_core == 1L, na.rm = TRUE)), by = .(protocol, uid)]
missed_counts[, missed_cat := fifelse(missed == 0, "0 missed",
                               fifelse(missed == 1, "1 missed", "2+ missed"))]

# Merge with subject_master for stratification
adherence_demo <- merge(missed_counts, subject_master, by = c("protocol", "uid"), all.x = TRUE)

# Summarize by treatment arm and protocol
adherence_summary <- adherence_demo %>%
  group_by(rx_code, protocol) %>%
  summarise(
    N = n(),
    n_0_missed = sum(missed_cat == "0 missed"),
    n_1_missed = sum(missed_cat == "1 missed"),
    n_2plus_missed = sum(missed_cat == "2+ missed"),
    pct_0_missed = round(100 * n_0_missed / N, 1),
    pct_1_missed = round(100 * n_1_missed / N, 1),
    pct_2plus_missed = round(100 * n_2plus_missed / N, 1),
    median_missed = median(missed, na.rm = TRUE),
    mean_missed = round(mean(missed, na.rm = TRUE), 2),
    sd_missed = round(sd(missed, na.rm = TRUE), 2)
  ) %>%
  ungroup()

kable(adherence_summary, caption = "Adherence Summary by Treatment Arm and Protocol")
```

**Explanation:** Summarizes adherence by treatment arm and protocol, listing how many people fall into each missed category plus summary statistics (mean/median/SD misses).


```{r compiled-table1, message=FALSE, eval=FALSE}
# dplyr loaded in setup
# knitr loaded in setup

# Prepare missed_counts with adherence categories
missed_counts <- infusions_only[, .(missed = sum(missed_infusion_core == 1L, na.rm = TRUE)), by = .(protocol, uid)]
missed_counts[, missed_cat := fifelse(missed == 0, "0 missed",
                               fifelse(missed == 1, "1 missed", "2+ missed"))]

# Merge with subject_master for demographics
demo <- merge(missed_counts, subject_master, by = c("protocol", "uid"), all.x = TRUE)

# Demographic summaries
n_total <- nrow(demo)
age_median <- median(demo$age, na.rm = TRUE)
age_iqr <- IQR(demo$age, na.rm = TRUE)
sex_tab <- table(demo$sex)
race_tab <- table(demo$race)
ethnicity_tab <- table(demo$ethnicity)
country_tab <- table(demo$country)
protocol_tab <- table(demo$protocol)
arm_tab <- table(demo$rx_code)

# Adherence summaries
n_0_missed <- sum(demo$missed_cat == "0 missed")
n_1_missed <- sum(demo$missed_cat == "1 missed")
n_2plus_missed <- sum(demo$missed_cat == "2+ missed")
mean_missed <- mean(demo$missed, na.rm = TRUE)
sd_missed <- sd(demo$missed, na.rm = TRUE)
median_missed <- median(demo$missed, na.rm = TRUE)
iqr_missed <- IQR(demo$missed, na.rm = TRUE)
retention <- round(100 * n_0_missed / n_total, 1)

# Compile into a single data frame
compiled_table <- data.frame(
  Variable = c(
    "Total Participants",
    "Age, median (IQR)",
    "Sex: Female, n (%)",
    "Sex: Male, n (%)",
    paste0("Race: ", paste(names(race_tab), collapse = ", ")),
    paste0("Ethnicity: ", paste(names(ethnicity_tab), collapse = ", ")),
    paste0("Country: ", paste(names(country_tab), collapse = ", ")),
    paste0("Protocol: ", paste(names(protocol_tab), collapse = ", ")),
    paste0("Treatment Arm: ", paste(names(arm_tab), collapse = ", ")),
    "0 Missed Infusions, n (%)",
    "1 Missed Infusion, n (%)",
    "2+ Missed Infusions, n (%)",
    "Missed Infusions, mean (SD)",
    "Missed Infusions, median (IQR)",
    "Retention (0 missed), %"
  ),
  Value = c(
    n_total,
    paste0(age_median, " (", age_iqr, ")"),
    paste0(sex_tab["Female"], " (", round(100*sex_tab["Female"]/n_total,1), "%)"),
    paste0(sex_tab["Male"], " (", round(100*sex_tab["Male"]/n_total,1), "%)"),
    paste(sapply(names(race_tab), function(x) paste0(x, ": ", race_tab[x], " (", round(100*race_tab[x]/n_total,1), "%)")), collapse = "; "),
    paste(sapply(names(ethnicity_tab), function(x) paste0(x, ": ", ethnicity_tab[x], " (", round(100*ethnicity_tab[x]/n_total,1), "%)")), collapse = "; "),
    paste(sapply(names(country_tab), function(x) paste0(x, ": ", country_tab[x], " (", round(100*country_tab[x]/n_total,1), "%)")), collapse = "; "),
    paste(sapply(names(protocol_tab), function(x) paste0(x, ": ", protocol_tab[x], " (", round(100*protocol_tab[x]/n_total,1), "%)")), collapse = "; "),
    paste(sapply(names(arm_tab), function(x) paste0(x, ": ", arm_tab[x], " (", round(100*arm_tab[x]/n_total,1), "%)")), collapse = "; "),
    paste0(n_0_missed, " (", round(100*n_0_missed/n_total,1), "%)"),
    paste0(n_1_missed, " (", round(100*n_1_missed/n_total,1), "%)"),
    paste0(n_2plus_missed, " (", round(100*n_2plus_missed/n_total,1), "%)"),
    paste0(round(mean_missed,2), " (", round(sd_missed,2), ")"),
    paste0(median_missed, " (", iqr_missed, ")"),
    retention
  )
)

kable(compiled_table, caption = "Comprehensive Demographics and Adherence Table (All Participants)")
```

**Explanation:** Creates a narrative-friendly summary table that combines key demographics and adherence statistics into one place.


```{r linear-regression-ae-missed, message=FALSE, eval=FALSE}
# data.table loaded in setup
# broom loaded in setup
# knitr loaded in setup
# ggplot2 loaded in setup

# Per-participant summary (if not already created)
ae_per_participant <- dt_reacto[rgsevmax > 0, .N, by = .(protocol, uid)]
setnames(ae_per_participant, "N", "Total_AEs")
missed_per_participant <- infusions_only[missed_infusion_core == 1L, .N, by = .(protocol, uid)]
setnames(missed_per_participant, "N", "Total_Missed_Infusions")
ae_missed_merged <- merge(ae_per_participant, missed_per_participant, by = c("protocol", "uid"), all = TRUE)
ae_missed_merged[is.na(Total_AEs), Total_AEs := 0]
ae_missed_merged[is.na(Total_Missed_Infusions), Total_Missed_Infusions := 0]

# Linear regression
lm_model <- lm(Total_Missed_Infusions ~ Total_AEs, data = ae_missed_merged)
lm_tidy <- tidy(lm_model, conf.int = TRUE)

# Present results
kable(lm_tidy, digits = 3, caption = "Linear Regression: Total Missed Infusions Predicted by Total AEs")

# Plot with regression line
ggplot(ae_missed_merged, aes(x = Total_AEs, y = Total_Missed_Infusions)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "blue") +
  labs(
    title = "Linear Regression: Missed Infusions vs. Total AEs",
    x = "Total AEs (per participant)",
    y = "Total Missed Infusions"
  ) +
  theme_minimal()
```

**Explanation:** Fits a simple linear regression to see how the number of adverse events per person relates to the number of missed infusions, and plots the relationship.


```{r aes-and-missed-by-infusion, message=FALSE, eval=FALSE}
# data.table loaded in setup
# ggplot2 loaded in setup
# tidyr loaded in setup
# knitr loaded in setup

# Number of AEs per infusion number
aes_by_infusion <- dt_reacto[rgsevmax > 0, .N, by = visitno]
setnames(aes_by_infusion, "N", "Total_AEs")

# Number of missed infusions per infusion number
missed_by_infusion <- infusions_only[missed_infusion_core == 1L, .N, by = infusion_num]
setnames(missed_by_infusion, "N", "Total_Missed_Infusions")

# Merge by infusion number
combined <- merge(
  aes_by_infusion, 
  missed_by_infusion, 
  by.x = "visitno", 
  by.y = "infusion_num", 
  all = TRUE
)
combined[is.na(Total_AEs), Total_AEs := 0]
combined[is.na(Total_Missed_Infusions), Total_Missed_Infusions := 0]

# Gather for plotting
combined_long <- combined %>%
  pivot_longer(cols = c("Total_AEs", "Total_Missed_Infusions"),
               names_to = "Type", values_to = "Count")

# Plot
ggplot(combined_long, aes(x = factor(visitno), y = Count, fill = Type)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8)) +
  labs(
    title = "AEs and Missed Infusions by Infusion Number",
    x = "Infusion Number",
    y = "Count",
    fill = "Type"
  ) +
  theme_minimal()

# Table
kable(combined, caption = "Total AEs and Missed Infusions by Infusion Number")
```

**Explanation:** Compares how many adverse events and missed infusions occur at each infusion number, prints the table, and plots the counts together.



```{r total-scheduled-visits-by-country, message=FALSE, eval=FALSE}
total_scheduled_by_country <- merged_data[
  , .(Total_Scheduled_Visits = .N),
  by = country
][order(-Total_Scheduled_Visits)]

kable(total_scheduled_by_country, caption = "Total Scheduled Visits by Country")

```

```{r computed-table1-xtable, message=FALSE, results='asis', echo=FALSE}
# Programmatic OR table for visit-level missed infusion model (clean-knit safe).
# Keep factor coding explicit so tidy term names match merge keys below.
table_model_data <- infusions_only[
  !age_bin %in% c("<18", ">50") &
    !is.na(age_bin) & !is.na(sex) & !is.na(country) & !is.na(rx_code) & !is.na(protocol),
  .(
    missed = as.integer(missed_infusion_core),
    age_bin, sex, country, rx_code, protocol, infusion_num,
    participant_id = interaction(protocol, uid, drop = TRUE)
  )
]

table_model_data[, age_bin := factor(as.character(age_bin),
  levels = c("18-25", "26-33", "34-41", "42-50"),
  ordered = FALSE
)]
table_model_data[, rx_code := factor(as.character(rx_code), levels = c("C3", "T1", "T2"))]
table_model_data[, sex := factor(as.character(sex))]
if ("Female" %in% levels(table_model_data$sex)) {
  table_model_data[, sex := stats::relevel(sex, ref = "Female")]
}
table_model_data[, infusion_num_f := factor(infusion_num)]
country_ref_table <- if ("United States" %in% unique(table_model_data$country)) {
  "United States"
} else {
  names(sort(table(table_model_data$country), decreasing = TRUE))[1]
}
table_model_data[, country := stats::relevel(factor(as.character(country)), ref = country_ref_table)]

table_model <- fit_mixed_logit(
  missed ~ age_bin + sex + rx_code + country + infusion_num_f + (1 | participant_id),
  data = table_model_data
)
table_model_tidy <- tidy_mixed_or(table_model)[, .(term, estimate, conf.low, conf.high, p.value)]

counts <- rbindlist(list(
  table_model_data[, .(
    Group = "Age Group",
    Level = as.character(age_bin),
    Total_Scheduled_Visits = .N,
    Missed = sum(missed),
    term = fifelse(as.character(age_bin) == "18-25", NA_character_, paste0("age_bin", as.character(age_bin)))
  ), by = age_bin],
  table_model_data[, .(
    Group = "Country",
    Level = as.character(country),
    Total_Scheduled_Visits = .N,
    Missed = sum(missed),
    term = fifelse(as.character(country) == country_ref_table, NA_character_, paste0("country", as.character(country)))
  ), by = country],
  table_model_data[, .(
    Group = "Sex",
    Level = as.character(sex),
    Total_Scheduled_Visits = .N,
    Missed = sum(missed),
    term = fifelse(as.character(sex) == if ("Female" %in% levels(table_model_data$sex)) "Female" else levels(table_model_data$sex)[1], NA_character_, paste0("sex", as.character(sex)))
  ), by = sex],
  table_model_data[, .(
    Group = "Treatment Arm",
    Level = as.character(rx_code),
    Total_Scheduled_Visits = .N,
    Missed = sum(missed),
    term = fifelse(as.character(rx_code) == "C3", NA_character_, paste0("rx_code", as.character(rx_code)))
  ), by = rx_code]
), fill = TRUE)

counts <- unique(counts)
counts[, Missed_Visits := sprintf("%s (%.1f%%)", format(Missed, big.mark = ","), 100 * Missed / Total_Scheduled_Visits)]

table_out <- merge(
  counts,
  table_model_tidy,
  by = "term",
  all.x = TRUE,
  sort = FALSE
)

# Preserve reference rows and surface missing estimates explicitly if a term did not match.
table_out[, OR_95CI := fifelse(
  is.na(term),
  "Reference",
  fifelse(
    is.na(estimate) | is.na(conf.low) | is.na(conf.high),
    "NA (NA--NA)",
    sprintf("%.2f (%.2f--%.2f)", estimate, conf.low, conf.high)
  )
)]
table_out[, P_value := fifelse(
  is.na(term),
  "---",
  fifelse(is.na(p.value), "NA", format.pval(p.value, digits = 3, eps = 0.001))
)]

table_out[, group_order := match(Group, c("Age Group", "Country", "Sex", "Treatment Arm"))]
table_out[Group == "Age Group", level_order := match(Level, c("18-25", "26-33", "34-41", "42-50"))]
table_out[Group == "Sex", level_order := match(Level, c("Female", "Male"))]
table_out[Group == "Treatment Arm", level_order := match(Level, c("C3", "T1", "T2"))]
table_out[Group == "Country", level_order := match(Level, sort(unique(Level)))]
setorder(table_out, group_order, level_order, Level)

table_out <- table_out[, .(Group, Level, Total_Scheduled_Visits, Missed_Visits, OR_95CI, P_value)]

# Keep LaTeX styling consistent with the legacy manuscript table.
xtab <- xtable(
  table_out,
  align = c("l", "l", "l", "r", "l", "l", "l")
)
print(
  xtab,
  include.rownames = FALSE,
  floating = TRUE,
  table.placement = "ht",
  hline.after = c(-1, 0, nrow(table_out)),
  comment = TRUE
)
```

```{r adjusted-sex-table, message=FALSE, eval=FALSE}
sex_table <- table_model_tidy[grepl("^sex", term)]

sex_table[
  ,
  `:=`(
    Variable     = sub("^sex", "Sex: ", term),
    `Odds Ratio` = sprintf("%.2f", estimate),
    `95% CI`     = sprintf("%.2f–%.2f", conf.low, conf.high),
    `p-value`    = format.pval(p.value, digits = 3, eps = 0.001)
  )
][
  ,
  .(Variable, `Odds Ratio`, `95% CI`, `p-value`)
] |>
  kable(caption = "Adjusted odds ratios for sex (from mixed-effects model)")
```
